### 2025-03-27 Quarto/paper.qmd
init

---
title: La Palma Earthquakes
author:
  - name: Steve Purves
    orcid: 0000-0002-0760-5497
    corresponding: true
    email: steve@curvenote.com
    roles:
      - Investigation
      - Project administration
      - Software
      - Visualization
    affiliations:
      - Curvenote
  - name: Rowan Cockett
    orcid: 0000-0002-7859-8394
    corresponding: false
    roles: []
    affiliations:
      - Curvenote
keywords:
  - La Palma
  - Earthquakes
abstract: |
  In September 2021, a significant jump in seismic activity on the island of La Palma (Canary Islands, Spain) signaled the start of a volcanic crisis that still continues at the time of writing. Earthquake data is continually collected and published by the Instituto Geográphico Nacional (IGN). ...
plain-language-summary: |
  Earthquake data for the island of La Palma from the September 2021 eruption is found ...
key-points:
  - A web scraping script was developed to pull data from the Instituto Geogràphico Nacional into a machine-readable form for analysis
  - Earthquake events on La Palma are consistent with the presence of both mantle and crustal reservoirs.
date: last-modified
citation:
  container-title: Earth and Space Science
---

# Example site and pdf

Lorem ipsum

## Example Subsection

Moar lorem ipsum

# Another Section

### 2025-03-27 _tex/paper.tex
Built site for gh-pages

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrreprt}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=0.5in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={La Palma Earthquakes},
  pdfauthor={Steve Purves; Rowan Cockett},
  pdfkeywords={La Palma, Earthquakes},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{La Palma Earthquakes}
\author{Steve Purves \and Rowan Cockett}
\date{2025-03-26}

\begin{document}
\maketitle
\begin{abstract}
In September 2021, a significant jump in seismic activity on the island
of La Palma (Canary Islands, Spain) signaled the start of a volcanic
crisis that still continues at the time of writing. Earthquake data is
continually collected and published by the Instituto Geográphico
Nacional (IGN). \ldots{}
\end{abstract}

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{2}
\tableofcontents
}
\chapter{Example site and pdf}\label{example-site-and-pdf}

Lorem ipsum

\section{Example Subsection}\label{example-subsection}

Moar lorem ipsum

\chapter{Another Section}\label{another-section}

\end{document}

### 2025-03-27 Quarto/paper.qmd
test changes
Fix generated site

@@
 ...
-plain-language-summary: |
-  Earthquake data for the island of La Palma from the September 2021 eruption is found ...
-key-points:
-  - A web scraping script was developed to pull data from the Instituto Geogràphico Nacional into a machine-readable form for analysis
-  - Earthquake events on La Palma are consistent with the presence of both mantle and crustal reservoirs.
 date: last-modified
@@
 
+Test update
+
+<!-- This shouldnt be seen, its a comment -->
+
 ## Example Subsection

### 2025-04-17 Quarto/paper.qmd
update paper.qmd based on paper references

@@
 ---
-title: La Palma Earthquakes
+title: Modeling Persuasion Behaviors in Social Deduction Games
 author:
-  - name: Steve Purves
-    orcid: 0000-0002-0760-5497
+  - name: First Author
+    orcid: 0000-0000-0000-0000
     corresponding: true
-    email: steve@curvenote.com
+    email: first.author@university.edu
     roles:
       - Investigation
-      - Project administration
+      - Methodology
       - Software
+      - Writing – original draft
       - Visualization
     affiliations:
-      - Curvenote
-  - name: Rowan Cockett
-    orcid: 0000-0002-7859-8394
+      - Department of Computer Science, University Name
+  - name: Second Author
+    orcid: 0000-0000-0000-0000
     corresponding: false
-    roles: []
+    email: second.author@university.edu
+    roles:
+      - Conceptualization
+      - Data Curation
+      - Writing – review & editing
+      - Project administration
     affiliations:
-      - Curvenote
+      - Department of Computer Science, University Name
 keywords:
-  - La Palma
-  - Earthquakes
+  - social deduction games
+  - persuasion modeling
+  - Werewolf Among Us dataset
+  - large language models
+  - multimodal analysis
 abstract: |
-  In September 2021, a significant jump in seismic activity on the island of La Palma (Canary Islands, Spain) signaled the start of a volcanic crisis that still continues at the time of writing.
-Earthquake data is continually collected and published by the Instituto Geográphico Nacional (IGN).
-...
+  This final project for CSCI‑5423 explores the modeling of persuasion behaviors in the text-based social deduction game Werewolf.
+We leverage the multimodal “Werewolf Among Us” dataset (Lai, 2022) and evaluate several large language models on their ability to persuade, deceive, and cooperate within game dialogues.
+Through a combination of feature engineering, sequence modeling, and reinforcement learning agents, we compare performance against baseline classifiers and analyze key linguistic strategies.
 date: last-modified
 citation:
-  container-title: Earth and Space Science
+  container-title: CSCI‑5423 Final Report
 ---
 
-# Example site and pdf
+# Introduction
 
-Lorem ipsum
+Introduce the motivation for studying persuasion in social deduction games. Describe the Werewolf game mechanics and why it offers a rich testbed for multimodal persuasion analysis.
 
-Test update
+# Related Work
 
-<!-- This shouldnt be seen, its a comment -->
+Review prior datasets and frameworks:
 
-## Example Subsection
+- Werewolf Among Us: dataset and original paper (Lai, 2022)
+- PersuasionGames repository and baseline models
+- AmongAgents and evaluation of LLMs in interactive text-based games (Chi, 2024)
+- RL approaches to strategic play in Werewolf (Xu et al., 2023)
+- Werewolf Arena framework by Google for LLM evaluation
 
-Moar lorem ipsum
+# Data and Preprocessing
 
-# Another Section
+Detail how we load and preprocess the HuggingFace Werewolf-Among-Us dataset. Include data splits, feature extraction, and any augmentation steps.
+
+# Methods
+
+Describe the modeling approaches:
+
+- Baseline classifiers (e.g., logistic regression, SVM)
+- Sequence models (e.g., LSTM, Transformer)
+- RL-based agent setup and reward definitions
+
+# Experiments and Evaluation
+
+Outline experimental setups:
+
+- Persuasion classification tasks
+- Game simulation with LLM agents
+- Metrics for persuasion success, deception detection, and cooperative play
+
+# Results
+
+Present quantitative results in tables and figures. Analyze which models and features best capture persuasion strategies.
+
+# Discussion
+
+Interpret findings, discuss limitations, and propose future work.
+
+# Conclusion
+
+Summarize contributions and insights from the project.
+
+# References
+
+Lai, B. (2022). Werewolf Among Us: A Multimodal Dataset for Modeling Persuasion Behaviors in Social Deduction Games. arXiv:2212.08279.
+
+Chi, Y. (2024). AmongAgents: Evaluating Large Language Models in the Interactive Text-Based Social Deduction Game. arXiv:2407.16521v2.
+
+Xu, Z., et al. (2023). Language Agents with Reinforcement Learning for Strategic Play in the Werewolf Game. arXiv:2310.18940v3.
+
+Blanchard, T., et al. (2024). Werewolf Arena: A Case Study in LLM Evaluation via Social Deduction. arXiv:2407.13943.
+
+---

### 2025-04-17 _tex/paper.tex
Built site for gh-pages

@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
 
@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 \makeatother
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
+
 \usepackage{bookmark}
@@
 \hypersetup{
-  pdftitle={La Palma Earthquakes},
-  pdfauthor={Steve Purves; Rowan Cockett},
-  pdfkeywords={La Palma, Earthquakes},
+  pdftitle={Modeling Persuasion Behaviors in Social Deduction Games},
+  pdfauthor={First Author; Second Author},
+  pdfkeywords={social deduction games, persuasion modeling, Werewolf
+Among Us dataset, large language models, multimodal analysis},
   colorlinks=true,
@@
 
-\title{La Palma Earthquakes}
-\author{Steve Purves \and Rowan Cockett}
-\date{2025-03-26}
+\title{Modeling Persuasion Behaviors in Social Deduction Games}
+\author{First Author \and Second Author}
+\date{2025-04-17}
 
@@
 \begin{abstract}
-In September 2021, a significant jump in seismic activity on the island
-of La Palma (Canary Islands, Spain) signaled the start of a volcanic
-crisis that still continues at the time of writing. Earthquake data is
-continually collected and published by the Instituto Geográphico
-Nacional (IGN). \ldots{}
+This final project for CSCI‑5423 explores the modeling of persuasion
+behaviors in the text-based social deduction game Werewolf. We leverage
+the multimodal ``Werewolf Among Us'' dataset (Lai, 2022) and evaluate
+several large language models on their ability to persuade, deceive, and
+cooperate within game dialogues. Through a combination of feature
+engineering, sequence modeling, and reinforcement learning agents, we
+compare performance against baseline classifiers and analyze key
+linguistic strategies.
 \end{abstract}
@@
 }
-\chapter{Example site and pdf}\label{example-site-and-pdf}
 
-Lorem ipsum
+\chapter{Introduction}\label{introduction}
 
-\section{Example Subsection}\label{example-subsection}
+Introduce the motivation for studying persuasion in social deduction
+games. Describe the Werewolf game mechanics and why it offers a rich
+testbed for multimodal persuasion analysis.
 
-Moar lorem ipsum
+\chapter{Related Work}\label{related-work}
 
-\chapter{Another Section}\label{another-section}
+Review prior datasets and frameworks:
+
+\begin{itemize}
+\tightlist
+\item
+  Werewolf Among Us: dataset and original paper (Lai, 2022)
+\item
+  PersuasionGames repository and baseline models
+\item
+  AmongAgents and evaluation of LLMs in interactive text-based games
+  (Chi, 2024)
+\item
+  RL approaches to strategic play in Werewolf (Xu et al., 2023)
+\item
+  Werewolf Arena framework by Google for LLM evaluation
+\end{itemize}
+
+\chapter{Data and Preprocessing}\label{data-and-preprocessing}
+
+Detail how we load and preprocess the HuggingFace Werewolf-Among-Us
+dataset. Include data splits, feature extraction, and any augmentation
+steps.
+
+\chapter{Methods}\label{methods}
+
+Describe the modeling approaches:
+
+\begin{itemize}
+\tightlist
+\item
+  Baseline classifiers (e.g., logistic regression, SVM)
+\item
+  Sequence models (e.g., LSTM, Transformer)
+\item
+  RL-based agent setup and reward definitions
+\end{itemize}
+
+\chapter{Experiments and Evaluation}\label{experiments-and-evaluation}
+
+Outline experimental setups:
+
+\begin{itemize}
+\tightlist
+\item
+  Persuasion classification tasks
+\item
+  Game simulation with LLM agents
+\item
+  Metrics for persuasion success, deception detection, and cooperative
+  play
+\end{itemize}
+
+\chapter{Results}\label{results}
+
+Present quantitative results in tables and figures. Analyze which models
+and features best capture persuasion strategies.
+
+\chapter{Discussion}\label{discussion}
+
+Interpret findings, discuss limitations, and propose future work.
+
+\chapter{Conclusion}\label{conclusion}
+
+Summarize contributions and insights from the project.
+
+\chapter{References}\label{references}
+
+Lai, B. (2022). Werewolf Among Us: A Multimodal Dataset for Modeling
+Persuasion Behaviors in Social Deduction Games. arXiv:2212.08279.
+
+Chi, Y. (2024). AmongAgents: Evaluating Large Language Models in the
+Interactive Text-Based Social Deduction Game. arXiv:2407.16521v2.
+
+Xu, Z., et al.~(2023). Language Agents with Reinforcement Learning for
+Strategic Play in the Werewolf Game. arXiv:2310.18940v3.
+
+Blanchard, T., et al.~(2024). Werewolf Arena: A Case Study in LLM
+Evaluation via Social Deduction. arXiv:2407.13943.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 

### 2025-04-23 Quarto/paper.qmd
Final EDA

@@
 ---
-title: Modeling Persuasion Behaviors in Social Deduction Games
+title: "The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games"
 author:
-  - name: First Author
-    orcid: 0000-0000-0000-0000
+  - name: Bhavana Jonnalagadda
+    orcid: 0009-0009-1054-0995
     corresponding: true
-    email: first.author@university.edu
-    roles:
-      - Investigation
-      - Methodology
-      - Software
-      - Writing – original draft
-      - Visualization
+    email: bhavana.jonnalagadda@colorado.edu
     affiliations:
-      - Department of Computer Science, University Name
-  - name: Second Author
-    orcid: 0000-0000-0000-0000
-    corresponding: false
-    email: second.author@university.edu
-    roles:
-      - Conceptualization
-      - Data Curation
-      - Writing – review & editing
-      - Project administration
+      - name: University of Colorado Boulder
+        id: 1
+        city: Boulder
+        state: CO
+  - name: Riley Jones
+    email: rjones@colorado.edu
     affiliations:
-      - Department of Computer Science, University Name
+      - id: 1
 keywords:

### 2025-04-23 _tex/paper.tex
Built site for gh-pages

@@
 \hypersetup{
-  pdftitle={Modeling Persuasion Behaviors in Social Deduction Games},
-  pdfauthor={First Author; Second Author},
+  pdftitle={The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games},
+  pdfauthor={Bhavana Jonnalagadda; Riley Jones},
   pdfkeywords={social deduction games, persuasion modeling, Werewolf
@@
 
-\title{Modeling Persuasion Behaviors in Social Deduction Games}
-\author{First Author \and Second Author}
-\date{2025-04-17}
+\title{The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games}
+\author{Bhavana Jonnalagadda \and Riley Jones}
+\date{2025-04-23}
 

### 2025-05-01 _tex/paper.tex
Built site for gh-pages

@@
+% Options for packages loaded elsewhere
 % Options for packages loaded elsewhere
@@
   numbers=noendperiod]{scrreprt}
-
+\usepackage{xcolor}
+\usepackage[margin=0.5in]{geometry}
 \usepackage{amsmath,amssymb}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 \makeatother
-\usepackage{xcolor}
-\usepackage[margin=0.5in]{geometry}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 % Make \paragraph and \subparagraph free-standing
@@
 
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatother
+
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
@@
 \makeatother
-
 \usepackage{bookmark}
-
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 \author{Bhavana Jonnalagadda \and Riley Jones}
-\date{2025-04-23}
-
+\date{2025-05-01}
 \begin{document}
@@
 \begin{abstract}
-This final project for CSCI‑5423 explores the modeling of persuasion
-behaviors in the text-based social deduction game Werewolf. We leverage
-the multimodal ``Werewolf Among Us'' dataset (Lai, 2022) and evaluate
-several large language models on their ability to persuade, deceive, and
-cooperate within game dialogues. Through a combination of feature
-engineering, sequence modeling, and reinforcement learning agents, we
-compare performance against baseline classifiers and analyze key
-linguistic strategies.
+Abstract TODO
 \end{abstract}
@@
 
-Introduce the motivation for studying persuasion in social deduction
-games. Describe the Werewolf game mechanics and why it offers a rich
-testbed for multimodal persuasion analysis.
-
-\chapter{Related Work}\label{related-work}
-
-Review prior datasets and frameworks:
+\begin{itemize}
+\tightlist
+\item
+  A description of the problem and its significance
+\item
+  How do LLMs function in a multi-agent environment?
 
@@
   \item
-  Werewolf Among Us: dataset and original paper (Lai, 2022)
+    Each has limited information
   \item
-  PersuasionGames repository and baseline models
+    Approximately the same ability, traits, skills
+  \end{itemize}
 \item
-  AmongAgents and evaluation of LLMs in interactive text-based games
-  (Chi, 2024)
+  We use LLMs to simulate whether synthetic agents can participate in
+  complex, adversarial group dynamics
 \item
-  RL approaches to strategic play in Werewolf (Xu et al., 2023)
-\item
-  Werewolf Arena framework by Google for LLM evaluation
-\end{itemize}
-
-\chapter{Data and Preprocessing}\label{data-and-preprocessing}
-
-Detail how we load and preprocess the HuggingFace Werewolf-Among-Us
-dataset. Include data splits, feature extraction, and any augmentation
-steps.
-
-\chapter{Methods}\label{methods}
-
-Describe the modeling approaches:
+  Werewolf is a good candiate for testing multi agent systems of
+  cooperation and secrecy
 
@@
   \item
-  Baseline classifiers (e.g., logistic regression, SVM)
+    Need citation
   \item
-  Sequence models (e.g., LSTM, Transformer)
-\item
-  RL-based agent setup and reward definitions
+    The game tests adaptive reasoning, strategic alignment, and
+    collective threat detection under special conditions
+  \end{itemize}
 \end{itemize}
 
-\chapter{Experiments and Evaluation}\label{experiments-and-evaluation}
+\section{Related Work}\label{related-work}
 
-Outline experimental setups:
+\subsection{Multi-Agent LLMs}\label{multi-agent-llms}
 
@@
 \item
-  Persuasion classification tasks
+  Among us game (\citeproc{ref-chiAMONGAGENTSEvaluatingLarge2024}{Chi,
+  Mao, and Tang 2024})
 \item
-  Game simulation with LLM agents
+  Collective problem solving
+  (\citeproc{ref-duLargeLanguageModels2024}{Du, Rajivan, and Gonzalez
+  2024})
+
+  \begin{itemize}
+  \tightlist
   \item
-  Metrics for persuasion success, deception detection, and cooperative
-  play
+    ``analyses indicate that LLM agent groups exhibit more
+    disagreements, complex statements, and a propensity for positive
+    statements compared to human groups''
+  \end{itemize}
+\item
+  Govsim (\citeproc{ref-piattiCooperateCollapseEmergence2024}{Piatti et
+  al. 2024})
+
+  \begin{itemize}
+  \tightlist
+  \item
+    ``In GOVSIM, a society of AI agents must collectively balance
+    exploiting a common resource with sustaining it for future use. This
+    environment enables the study of how ethical considerations,
+    strategic planning, and negotiation skills impact cooperative
+    outcomes.''
+  \end{itemize}
+\item
+  All found similar themes
+
+  \begin{itemize}
+  \tightlist
+  \item
+    That LLMs are capable and good at understanding the rules
+  \item
+    That they can cooperate and be sneaky
+  \end{itemize}
+\end{itemize}
+
+\subsection{LLMs and Werewolf}\label{llms-and-werewolf}
+
+\begin{itemize}
+\tightlist
+\item
+  Examination of improving werewolf by LLMs
+  (\citeproc{ref-xuLanguageAgentsReinforcement2024}{Xu et al. 2024})
+
+  \begin{itemize}
+  \tightlist
+  \item
+    ``our agents use an LLM to perform deductive reasoning and generate
+    a diverse set of action candidates. Then an RL policy trained to
+    optimize the decision-making ability chooses an action from the
+    candidates to play in the game. Extensive experiments show that our
+    agents overcome the intrinsic bias and outperform existing LLM-based
+    agents in the Werewolf game.''
+  \end{itemize}
+\item
+  Werewolf Arena (\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis,
+  Friedhoff, and Chen 2024})
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Used in this paper
+  \end{itemize}
+\item
+  Explicitly discuss how none of the exisiting LLM+Werewolf papers
+  examine the differences/compare from a human dataset
+\end{itemize}
+
+\chapter{Methods}\label{methods}
+
+\section{Data}\label{data}
+
+\subsection{Werewolf Among Us Human
+Dataset}\label{werewolf-among-us-human-dataset}
+
+\begin{itemize}
+\tightlist
+\item
+  Human dataset description
+  (\citeproc{ref-laiWerewolfUsMultimodal2022}{Lai et al. 2022})
+\item
+  Is specifically for a form of one-night werewolf
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Describe key differences
+  \end{itemize}
+\item
+  Used specifically for the text available
+
+  \begin{itemize}
+  \tightlist
+  \item
+    and annotations of persuasion strategy on the text
+  \end{itemize}
+\end{itemize}
+
+\subsection{Werewolf Arena}\label{werewolf-arena}
+
+\begin{itemize}
+\tightlist
+\item
+  (\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and
+  Chen 2024})
+\item
+  Discuss the framework, how it works, prompts, etc
+\item
+  Discuss what types of runs we did
+\item
+  Discuss the data included in output
+\item
+  Talk about how we had to annotate the LLM speech with persuasion
+  strategies ourselves
+\end{itemize}
+
+\section{Analysis}\label{analysis}
+
+\begin{itemize}
+\tightlist
+\item
+  Formatted data to match, performed various comparisons
 \end{itemize}
@@
 
-Present quantitative results in tables and figures. Analyze which models
-and features best capture persuasion strategies.
+\begin{figure}[H]
 
-\chapter{Discussion}\label{discussion}
+\centering{
+
+\centering{
+
+\begin{verbatim}
+Unable to display output for mime type(s): text/html
+\end{verbatim}
+
+}
+
+\subcaption{\label{fig-llm-winrounds-1}The LLM wins, by how many rounds
+that partiticular game had.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-llm-winrounds-output-2.png}}
+
+}
+
+\subcaption{\label{fig-llm-winrounds-2}}
+
+}
+
+\caption{\label{fig-llm-winrounds}}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://CUBoulder-DS.github.io/CSCI-5423-Final/Data/EDA_Comparison-preview.html\#cell-fig-llm-winrounds}{Werewolf
+Among Us: Human vs LLM Analysis}}
+
+\begin{figure}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-stratbyrole-hum-output-1.png}}
+
+}
+
+\caption{\label{fig-stratbyrole-hum}}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://CUBoulder-DS.github.io/CSCI-5423-Final/Data/EDA_Comparison-preview.html\#cell-fig-stratbyrole-hum}{Werewolf
+Among Us: Human vs LLM Analysis}}
+
+\begin{figure}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-stratbyrole-llms-output-1.png}}
+
+}
+
+\caption{\label{fig-stratbyrole-llms}}
+
+\end{figure}%
+
+\textsubscript{Source:
+\href{https://CUBoulder-DS.github.io/CSCI-5423-Final/Data/EDA_Comparison-preview.html\#cell-fig-stratbyrole-llms}{Werewolf
+Among Us: Human vs LLM Analysis}}
+
+\chapter{Discussion and Conclusion}\label{discussion-and-conclusion}
 
@@
 
-\chapter{Conclusion}\label{conclusion}
+\section{Limitations}\label{limitations}
+
+\section{Future Work}\label{future-work}
+
+\section{Summary}\label{summary}
 
@@
 
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
 \chapter{References}\label{references}
 
-Lai, B. (2022). Werewolf Among Us: A Multimodal Dataset for Modeling
-Persuasion Behaviors in Social Deduction Games. arXiv:2212.08279.
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-bailisWerewolfArenaCase2024}
+Bailis, Suma, Jane Friedhoff, and Feiyang Chen. 2024. {``Werewolf
+{Arena}: {A Case Study} in {LLM Evaluation} via {Social Deduction}.''}
+July 18, 2024. \url{https://doi.org/10.48550/arXiv.2407.13943}.
 
-Chi, Y. (2024). AmongAgents: Evaluating Large Language Models in the
-Interactive Text-Based Social Deduction Game. arXiv:2407.16521v2.
+\bibitem[\citeproctext]{ref-chiAMONGAGENTSEvaluatingLarge2024}
+Chi, Yizhou, Lingjun Mao, and Zineng Tang. 2024. {``{AMONGAGENTS}:
+{Evaluating Large Language Models} in the {Interactive Text-Based Social
+Deduction Game}.''} July 24, 2024.
+\url{https://doi.org/10.48550/arXiv.2407.16521}.
 
-Xu, Z., et al.~(2023). Language Agents with Reinforcement Learning for
-Strategic Play in the Werewolf Game. arXiv:2310.18940v3.
+\bibitem[\citeproctext]{ref-choRoundTableInvestigatingGroup2024}
+Cho, Young-Min, Raphael Shu, Nilaksh Das, Tamer Alkhouli, Yi-An Lai,
+Jason Cai, Monica Sunkara, and Yi Zhang. 2024. {``{RoundTable}:
+{Investigating Group Decision-Making Mechanism} in {Multi-Agent
+Collaboration}.''} November 11, 2024.
+\url{https://doi.org/10.48550/arXiv.2411.07161}.
 
-Blanchard, T., et al.~(2024). Werewolf Arena: A Case Study in LLM
-Evaluation via Social Deduction. arXiv:2407.13943.
+\bibitem[\citeproctext]{ref-duLargeLanguageModels2024}
+Du, Yinuo, Prashanth Rajivan, and Cleotilde Gonzalez. 2024. {``Large
+{Language Models} for {Collective Problem-Solving}: {Insights} into
+{Group Consensus Decision-Making}.''} \emph{Proceedings of the Annual
+Meeting of the Cognitive Science Society} 46 (0).
+\url{https://escholarship.org/uc/item/6s060914}.
+
+\bibitem[\citeproctext]{ref-laiWerewolfUsMultimodal2022}
+Lai, Bolin, Hongxin Zhang, Miao Liu, Aryan Pariani, Fiona Ryan, Wenqi
+Jia, Shirley Anugrah Hayati, James M. Rehg, and Diyi Yang. 2022.
+{``Werewolf {Among Us}: {A Multimodal Dataset} for {Modeling Persuasion
+Behaviors} in {Social Deduction Games}.''} December 16, 2022.
+\url{https://doi.org/10.48550/arXiv.2212.08279}.
+
+\bibitem[\citeproctext]{ref-piattiCooperateCollapseEmergence2024}
+Piatti, Giorgio, Zhijing Jin, Max Kleiman-Weiner, Bernhard Schölkopf,
+Mrinmaya Sachan, and Rada Mihalcea. 2024. {``Cooperate or {Collapse}:
+{Emergence} of {Sustainable Cooperation} in a {Society} of {LLM
+Agents}.''} \emph{Advances in Neural Information Processing Systems} 37
+(December): 111715--59.
+\url{https://proceedings.neurips.cc/paper_files/paper/2024/hash/ca9567d8ef6b2ea2da0d7eed57b933ee-Abstract-Conference.html}.
+
+\bibitem[\citeproctext]{ref-xuLanguageAgentsReinforcement2024}
+Xu, Zelai, Chao Yu, Fei Fang, Yu Wang, and Yi Wu. 2024. {``Language
+{Agents} with {Reinforcement Learning} for {Strategic Play} in the
+{Werewolf Game}.''} February 20, 2024.
+\url{https://doi.org/10.48550/arXiv.2310.18940}.
+
+\end{CSLReferences}
 
@@
 
+\chapter{Project Contributions}\label{project-contributions}
+
+\textbf{Bhavana Jonnalagadda}:
+
+\begin{itemize}
+\tightlist
+\item
+  Paper framework (Quarto) setup
+\item
+  Github repo management
+\item
+  EDA on LLM dataset
+\item
+  Final comparison EDA and results analysis
+\item
+  Results section
+\item
+  Discussion and Conclusion section
+\item
+  Abstract
+\end{itemize}
+
+\textbf{Riley Jones}:
+
+\begin{itemize}
+\tightlist
+\item
+  EDA on human dataset
+\item
+  Werewolf Arena LLM simulation running and data aquisition
+\item
+  Introduction section
+\item
+  Methods section
+\end{itemize}
+
 \end{document}

### 2025-05-05 Quarto/paper.qmd

--- 2025-03-27 Quarto/paper.qmd
@@
 ---
-title: La Palma Earthquakes
+title: "The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games"
 author:
-  - name: Steve Purves
-    orcid: 0000-0002-0760-5497
+  - name: Bhavana Jonnalagadda
+    orcid: 0009-0009-1054-0995
     corresponding: true
-    email: steve@curvenote.com
-    roles:
-      - Investigation
-      - Project administration
-      - Software
-      - Visualization
+    email: bhavana.jonnalagadda@colorado.edu
     affiliations:
-      - Curvenote
-  - name: Rowan Cockett
-    orcid: 0000-0002-7859-8394
-    corresponding: false
-    roles: []
+      - name: University of Colorado Boulder
+        id: 1
+        city: Boulder
+        state: CO
+  - name: Riley Jones
+    email: rjones@colorado.edu
     affiliations:
-      - Curvenote
+      - id: 1
 keywords:
-  - La Palma
-  - Earthquakes
+  - social deduction games
+  - persuasion modeling
+  - Werewolf Among Us dataset
+  - large language models
+  - multimodal analysis
 abstract: |
-  In September 2021, a significant jump in seismic activity on the island of La Palma (Canary Islands, Spain) signaled the start of a volcanic crisis that still continues at the time of writing.
-Earthquake data is continually collected and published by the Instituto Geográphico Nacional (IGN).
-...
+  Abstract TODO
 date: last-modified
 citation:
-  container-title: Earth and Space Science
+  container-title: Human vs LLM Multi-Agent Games
 ---
 
-# Example site and pdf
+::: {.content-visible when-format="html"}
+::: {.column-margin}
+![](Images/logo.png)
+:::
+:::
 
-Lorem ipsum
+# Introduction
 
-Test update
+<!-- TODO: Broken for some reason?!?!? Fix -->
+<!-- ::: {.content-hidden unless-format="latex"}
+::: {.callout-tip}
+## View Online
+This PDF's content, the source code notebooks, along with live interactive versions of all figures (and more!) is available at the website version of this paper: [https://cuboulder-ds.github.io/CSCI-5423-Final](https://cuboulder-ds.github.io/CSCI-5423-Final)
+:::
+::: -->
 
-<!-- This shouldnt be seen, its a comment -->
+- A description of the problem and its significance
+- How do LLMs function in a multi-agent environment?
+  - Each has limited information
+  - Approximately the same ability, traits, skills
+- We use LLMs to simulate whether synthetic agents can participate in complex, adversarial group dynamics
+- Werewolf is a good candiate for testing multi agent systems of cooperation and secrecy
+  - Need citation
+  - The game tests adaptive reasoning, strategic alignment, and collective threat detection under special conditions
 
-## Example Subsection
+## Related Work
 
-Moar lorem ipsum
+### Multi-Agent LLMs
 
-# Another Section
+- Among us game [@chiAMONGAGENTSEvaluatingLarge2024]
+- Collective problem solving [@duLargeLanguageModels2024]
+  - "analyses indicate that LLM agent groups exhibit more disagreements, complex statements, and a propensity for positive statements compared to human groups"
+- Govsim [@piattiCooperateCollapseEmergence2024]
+  - "In GOVSIM, a society of AI agents must collectively balance exploiting a common resource with sustaining it for future use.
+This environment enables the study of how ethical considerations, strategic planning, and negotiation skills impact cooperative outcomes."
+- All found similar themes
+  - That LLMs are capable and good at understanding the rules
+  - That they can cooperate and be sneaky
+
+### LLMs and Werewolf
+
+- Examination of improving werewolf by LLMs [@xuLanguageAgentsReinforcement2024]
+  - "our agents use an LLM to perform deductive reasoning and generate a diverse set of action candidates.
+Then an RL policy trained to optimize the decision-making ability chooses an action from the candidates to play in the game.
+Extensive experiments show that our agents overcome the intrinsic bias and outperform existing LLM-based agents in the Werewolf game."
+- Werewolf Arena [@bailisWerewolfArenaCase2024]
+  - Used in this paper
+- Explicitly discuss how none of the exisiting LLM+Werewolf papers examine the differences/compare from a human dataset
+
+# Methods
+
+## Data
+
+### Werewolf Among Us Human Dataset
+
+- Human dataset description [@laiWerewolfUsMultimodal2022]
+- Is specifically for a form of one-night werewolf
+  - Describe key differences
+- Used specifically for the text available
+  - and annotations of persuasion strategy on the text
+
+### Werewolf Arena
+
+- [@bailisWerewolfArenaCase2024]
+- Discuss the framework, how it works, prompts, etc
+- Discuss what types of runs we did
+- Discuss the data included in output
+- Talk about how we had to annotate the LLM speech with persuasion strategies ourselves
+
+## Analysis
+
+- Formatted data to match, performed various comparisons
+
+# Results
+
+{{< embed Data/EDA_Comparison.ipynb#fig-llm-winrounds >}}
+
+{{< embed Data/EDA_Comparison.ipynb#fig-stratbyrole-hum >}}
+{{< embed Data/EDA_Comparison.ipynb#fig-stratbyrole-llms >}}
+
+# Discussion and Conclusion
+
+Interpret findings, discuss limitations, and propose future work.
+
+## Limitations
+
+## Future Work
+
+## Summary
+
+Summarize contributions and insights from the project.
+
+---
+
+<!-- See https://quarto.org/docs/authoring/citations.html -->
+# References
+
+::: {#refs}
+:::
+
+---
+
+# Project Contributions
+
+**Bhavana Jonnalagadda**:
+
+- Paper framework (Quarto) setup
+- Github repo management
+- EDA on LLM dataset
+- Final comparison EDA and results analysis
+- Results section
+- Discussion and Conclusion section
+- Abstract
+
+**Riley Jones**:
+
+- EDA on human dataset
+- Werewolf Arena LLM simulation running and data aquisition
+- Introduction section
+- Methods section

### 2025-05-06 Quarto/paper.qmd
Introduction

@@
 
-- A description of the problem and its significance
-- How do LLMs function in a multi-agent environment?
-  - Each has limited information
-  - Approximately the same ability, traits, skills
-- We use LLMs to simulate whether synthetic agents can participate in complex, adversarial group dynamics
-- Werewolf is a good candiate for testing multi agent systems of cooperation and secrecy
-  - Need citation
-  - The game tests adaptive reasoning, strategic alignment, and collective threat detection under special conditions
+- Social deduction games like _Werewolf_ offer a clear way to evaluate how agents deceive, persuade, and reason in group settings[@wikiwerewolf].
+In these games, players have limited information, hidden identities, and must convince others while trying to figure out who is lying.
+These challenges closely match real life situations involving trust, negotiation, and manipulation.
+
+- We wanted to compare how humans and large language models (LLMs) handle these situations. To do this, we used two recent datasets: 
+	- _Werewolf Among Us_ (Lai et al., 2022), a collection of real human gameplay annotated with persuasion strategies, 
+	- _Werewolf Arena_ (Bailis et al., 2024), a simulated environment where LLM agents play the game autonomously. 
+	- While both studies show Werewolf generates complex strategic language, neither compares human and LLM behavior directly.
+
+- Our project addresses this gap.
+We analyzed transcripts from both datasets, matched them by role, round, and persuasion strategy, and compared how humans and LLMs lie, persuade, and detect deception.
+- By annotating utterances with the same set of persuasive strategies, we clearly show how synthetic agents differ from or resemble humans when navigating deception in adversarial group interactions.
 

### 2025-05-06 _tex/paper.tex
Built site for gh-pages

@@
 \author{Bhavana Jonnalagadda \and Riley Jones}
-\date{2025-05-01}
+\date{2025-05-06}
 \begin{document}
@@
 \begin{itemize}
-\tightlist
 \item
-  A description of the problem and its significance
+  Social deduction games like \emph{Werewolf} offer a clear way to
+  evaluate how agents deceive, persuade, and reason in group
+  settings(\citeproc{ref-wikiwerewolf}{Wikipedia contributors 2024}). In
+  these games, players have limited information, hidden identities, and
+  must convince others while trying to figure out who is lying. These
+  challenges closely match real life situations involving trust,
+  negotiation, and manipulation.
 \item
-  How do LLMs function in a multi-agent environment?
+  We wanted to compare how humans and large language models (LLMs)
+  handle these situations. To do this, we used two recent datasets:
 
@@
   \item
-    Each has limited information
+    \emph{Werewolf Among Us} (Lai et al., 2022), a collection of real
+    human gameplay annotated with persuasion strategies,
   \item
-    Approximately the same ability, traits, skills
+    \emph{Werewolf Arena} (Bailis et al., 2024), a simulated environment
+    where LLM agents play the game autonomously.
+  \item
+    While both studies show Werewolf generates complex strategic
+    language, neither compares human and LLM behavior directly.
   \end{itemize}
 \item
-  We use LLMs to simulate whether synthetic agents can participate in
-  complex, adversarial group dynamics
+  Our project addresses this gap. We analyzed transcripts from both
+  datasets, matched them by role, round, and persuasion strategy, and
+  compared how humans and LLMs lie, persuade, and detect deception.
 \item
-  Werewolf is a good candiate for testing multi agent systems of
-  cooperation and secrecy
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Need citation
-  \item
-    The game tests adaptive reasoning, strategic alignment, and
-    collective threat detection under special conditions
-  \end{itemize}
+  By annotating utterances with the same set of persuasive strategies,
+  we clearly show how synthetic agents differ from or resemble humans
+  when navigating deception in adversarial group interactions.
 \end{itemize}
@@
 
+\bibitem[\citeproctext]{ref-wikiwerewolf}
+Wikipedia contributors. 2024. {``Mafia (Party Game).''}
+\url{https://en.wikipedia.org/wiki/Mafia_(party_game)}.
+
 \bibitem[\citeproctext]{ref-xuLanguageAgentsReinforcement2024}

### 2025-05-06 Quarto/paper.qmd
Methods

@@
 
-- We wanted to compare how humans and large language models (LLMs) handle these situations. To do this, we used two recent datasets: 
+- We wanted to compare how humans and large language models (LLMs) handle these situations. To do this, we used a recent human dataset and constructed one from an LLM-based simulator: 
 	- _Werewolf Among Us_ (Lai et al., 2022), a collection of real human gameplay annotated with persuasion strategies, 
@@
 
-- Human dataset description [@laiWerewolfUsMultimodal2022]
-- Is specifically for a form of one-night werewolf
-  - Describe key differences
-- Used specifically for the text available
-  - and annotations of persuasion strategy on the text
+We used the _Werewolf Among Us_ dataset (Lai et al., 2022), which contains annotated dialogues from over 150 real games of One Night Werewolf and Avalon.
+These games differ from classic Werewolf because they have only one round of discussion and voting, do not eliminate players during the game, and include many specialized roles beyond Villager and Werewolf.
+The dataset provides detailed annotations of persuasion strategies for each utterance, such as accusations, defenses, and identity claims.
+We specifically used the textual transcriptions and their strategy annotations for our comparisons.
 
-### Werewolf Arena
+### Werewolf Arena (LLM Dataset)
 
-- [@bailisWerewolfArenaCase2024]
-- Discuss the framework, how it works, prompts, etc
-- Discuss what types of runs we did
-- Discuss the data included in output
-- Talk about how we had to annotate the LLM speech with persuasion strategies ourselves
+The _Werewolf Arena_ dataset (Bailis et al., 2024) features simulated classic Werewolf games played by LLM agents without human intervention.
+Unlike the one-round human games, these simulations involve multiple rounds alternating between night (secret actions) and day (open discussion).
+Each LLM agent is assigned a role (Villager, Werewolf, Seer, Doctor) and receives context-specific prompts that guide their strategic interactions.
+
+We ran simulations using five LLM models: GPT-4o, GPT-4.1, GPT-4o-mini, DeepSeek-Chat, and DeepSeek-Reasoner. We experimented with two configurations:
+
+- 8 players with 8 rounds of discussion
+
+- 10 players with 6 rounds of discussion
+
+We chose these configurations to give villagers more time to coordinate, extending the dialogue to better observe persuasive behaviors.
+After running the simulations, we manually annotated the LLM-generated dialogue using the same persuasion categories as in the human dataset.
 
@@
 
-- Formatted data to match, performed various comparisons
+We standardized annotations across both datasets so they could be directly compared.
+Our analyses focused on frequency distributions of persuasion strategies, comparisons by role (villager versus werewolf), and differences in how humans and LLMs applied these strategies.
 

### 2025-05-06 _tex/paper.tex
Built site for gh-pages

@@
   We wanted to compare how humans and large language models (LLMs)
-  handle these situations. To do this, we used two recent datasets:
+  handle these situations. To do this, we used a recent human dataset
+  and constructed one from an LLM-based simulator:
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Human dataset description
-  (\citeproc{ref-laiWerewolfUsMultimodal2022}{Lai et al. 2022})
-\item
-  Is specifically for a form of one-night werewolf
+We used the \emph{Werewolf Among Us} dataset (Lai et al., 2022), which
+contains annotated dialogues from over 150 real games of One Night
+Werewolf and Avalon. These games differ from classic Werewolf because
+they have only one round of discussion and voting, do not eliminate
+players during the game, and include many specialized roles beyond
+Villager and Werewolf. The dataset provides detailed annotations of
+persuasion strategies for each utterance, such as accusations, defenses,
+and identity claims. We specifically used the textual transcriptions and
+their strategy annotations for our comparisons.
+
+\subsection{Werewolf Arena (LLM
+Dataset)}\label{werewolf-arena-llm-dataset}
+
+The \emph{Werewolf Arena} dataset (Bailis et al., 2024) features
+simulated classic Werewolf games played by LLM agents without human
+intervention. Unlike the one-round human games, these simulations
+involve multiple rounds alternating between night (secret actions) and
+day (open discussion). Each LLM agent is assigned a role (Villager,
+Werewolf, Seer, Doctor) and receives context-specific prompts that guide
+their strategic interactions.
+
+We ran simulations using five LLM models: GPT-4o, GPT-4.1, GPT-4o-mini,
+DeepSeek-Chat, and DeepSeek-Reasoner. We experimented with two
+configurations:
 
 \begin{itemize}
-  \tightlist
 \item
-    Describe key differences
-  \end{itemize}
+  8 players with 8 rounds of discussion
 \item
-  Used specifically for the text available
-
-  \begin{itemize}
-  \tightlist
-  \item
-    and annotations of persuasion strategy on the text
-  \end{itemize}
+  10 players with 6 rounds of discussion
 \end{itemize}
 
-\subsection{Werewolf Arena}\label{werewolf-arena}
-
-\begin{itemize}
-\tightlist
-\item
-  (\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and
-  Chen 2024})
-\item
-  Discuss the framework, how it works, prompts, etc
-\item
-  Discuss what types of runs we did
-\item
-  Discuss the data included in output
-\item
-  Talk about how we had to annotate the LLM speech with persuasion
-  strategies ourselves
-\end{itemize}
+We chose these configurations to give villagers more time to coordinate,
+extending the dialogue to better observe persuasive behaviors. After
+running the simulations, we manually annotated the LLM-generated
+dialogue using the same persuasion categories as in the human dataset.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Formatted data to match, performed various comparisons
-\end{itemize}
+We standardized annotations across both datasets so they could be
+directly compared. Our analyses focused on frequency distributions of
+persuasion strategies, comparisons by role (villager versus werewolf),
+and differences in how humans and LLMs applied these strategies.
 

### 2025-05-06 Quarto/paper.qmd
Fix citations in Methods and Introduction

@@
 - We wanted to compare how humans and large language models (LLMs) handle these situations. To do this, we used a recent human dataset and constructed one from an LLM-based simulator: 
-	- _Werewolf Among Us_ (Lai et al., 2022), a collection of real human gameplay annotated with persuasion strategies, 
-	- _Werewolf Arena_ (Bailis et al., 2024), a simulated environment where LLM agents play the game autonomously. 
+	- _Werewolf Among Us_ [@laiWerewolfUsMultimodal2022], a collection of real human gameplay annotated with persuasion strategies, 
+	- _Werewolf Arena_ [@bailisWerewolfArenaCase2024], a simulated environment where LLM agents play the game autonomously. 
 	- While both studies show Werewolf generates complex strategic language, neither compares human and LLM behavior directly.
@@
 
-We used the _Werewolf Among Us_ dataset (Lai et al., 2022), which contains annotated dialogues from over 150 real games of One Night Werewolf and Avalon.
+We used the _Werewolf Among Us_ dataset [@laiWerewolfUsMultimodal2022], which contains annotated dialogues from over 150 real games of One Night Werewolf and Avalon.
 These games differ from classic Werewolf because they have only one round of discussion and voting, do not eliminate players during the game, and include many specialized roles beyond Villager and Werewolf.
@@
 
-The _Werewolf Arena_ dataset (Bailis et al., 2024) features simulated classic Werewolf games played by LLM agents without human intervention.
+The _Werewolf Arena_ dataset [@bailisWerewolfArenaCase2024] features simulated classic Werewolf games played by LLM agents without human intervention.
 Unlike the one-round human games, these simulations involve multiple rounds alternating between night (secret actions) and day (open discussion).

### 2025-05-06 _tex/paper.tex
Built site for gh-pages

@@
   \item
-    \emph{Werewolf Among Us} (Lai et al., 2022), a collection of real
-    human gameplay annotated with persuasion strategies,
+    \emph{Werewolf Among Us}
+    (\citeproc{ref-laiWerewolfUsMultimodal2022}{Lai et al. 2022}), a
+    collection of real human gameplay annotated with persuasion
+    strategies,
   \item
-    \emph{Werewolf Arena} (Bailis et al., 2024), a simulated environment
-    where LLM agents play the game autonomously.
+    \emph{Werewolf Arena}
+    (\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and
+    Chen 2024}), a simulated environment where LLM agents play the game
+    autonomously.
   \item
@@
 
-We used the \emph{Werewolf Among Us} dataset (Lai et al., 2022), which
+We used the \emph{Werewolf Among Us} dataset
+(\citeproc{ref-laiWerewolfUsMultimodal2022}{Lai et al. 2022}), which
 contains annotated dialogues from over 150 real games of One Night
@@
 
-The \emph{Werewolf Arena} dataset (Bailis et al., 2024) features
-simulated classic Werewolf games played by LLM agents without human
-intervention. Unlike the one-round human games, these simulations
-involve multiple rounds alternating between night (secret actions) and
-day (open discussion). Each LLM agent is assigned a role (Villager,
-Werewolf, Seer, Doctor) and receives context-specific prompts that guide
-their strategic interactions.
+The \emph{Werewolf Arena} dataset
+(\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and Chen
+2024}) features simulated classic Werewolf games played by LLM agents
+without human intervention. Unlike the one-round human games, these
+simulations involve multiple rounds alternating between night (secret
+actions) and day (open discussion). Each LLM agent is assigned a role
+(Villager, Werewolf, Seer, Doctor) and receives context-specific prompts
+that guide their strategic interactions.
 

### 2025-05-06 Quarto/paper.qmd
add orcid to qmd file

@@
   - name: Riley Jones
+    orcid: 0009-0001-8160-5508
     email: rjones@colorado.edu

### 2025-05-07 Quarto/paper.qmd
Update Intro, Methods, WWA GUI figure

@@
 
-- Social deduction games like _Werewolf_ offer a clear way to evaluate how agents deceive, persuade, and reason in group settings[@wikiwerewolf].
-In these games, players have limited information, hidden identities, and must convince others while trying to figure out who is lying.
-These challenges closely match real life situations involving trust, negotiation, and manipulation.
-
-- We wanted to compare how humans and large language models (LLMs) handle these situations. To do this, we used a recent human dataset and constructed one from an LLM-based simulator: 
-	- _Werewolf Among Us_ [@laiWerewolfUsMultimodal2022], a collection of real human gameplay annotated with persuasion strategies, 
-	- _Werewolf Arena_ [@bailisWerewolfArenaCase2024], a simulated environment where LLM agents play the game autonomously. 
-	- While both studies show Werewolf generates complex strategic language, neither compares human and LLM behavior directly.
-
-- Our project addresses this gap.
-We analyzed transcripts from both datasets, matched them by role, round, and persuasion strategy, and compared how humans and LLMs lie, persuade, and detect deception.
-- By annotating utterances with the same set of persuasive strategies, we clearly show how synthetic agents differ from or resemble humans when navigating deception in adversarial group interactions.
+Social deduction games like Werewolf offer a clear way to evaluate how agents deceive, persuade, and reason in group settings [@wikiwerewolf].
+In these games, players operate with limited information and hidden identities, attempting to convince others while trying to uncover deception themselves.
+These dynamics mirror real-world challenges involving trust, negotiation, and manipulation.
+To explore how humans and large language models (LLMs) navigate such scenarios, we analyzed two key datasets: Werewolf Among Us [@laiWerewolfUsMultimodal2022], which features real human gameplay annotated with persuasion strategies, and Werewolf Arena [@bailisWerewolfArenaCase2024], a simulated environment in which LLM agents autonomously play the game.
+While both studies demonstrate that Werewolf elicits rich, strategic language, neither directly compares human and LLM behavior.
+Our project fills this gap.
+We analyzed transcripts from both datasets, aligning them by role, round, and persuasive strategy, and compared how humans and LLMs lie, persuade, and detect deception.
+By annotating all utterances using a consistent taxonomy of persuasive strategies, we expose key differences and similarities in how synthetic agents and humans handle adversarial group interactions.
 
@@
 
-We used the _Werewolf Among Us_ dataset [@laiWerewolfUsMultimodal2022], which contains annotated dialogues from over 150 real games of One Night Werewolf and Avalon.
-These games differ from classic Werewolf because they have only one round of discussion and voting, do not eliminate players during the game, and include many specialized roles beyond Villager and Werewolf.
-The dataset provides detailed annotations of persuasion strategies for each utterance, such as accusations, defenses, and identity claims.
-We specifically used the textual transcriptions and their strategy annotations for our comparisons.
+We used the *Werewolf Among Us* dataset \[@laiWerewolfUsMultimodal2022], containing annotated dialogues from over 150 real games of One Night Werewolf and Avalon.
+These games differ from classic Werewolf by having only one round of discussion and voting, not eliminating players during gameplay, and featuring specialized roles beyond Villager and Werewolf.
+The dataset includes detailed annotations of persuasion strategies for each utterance, such as accusations, defenses, and identity claims.
+Our analysis specifically utilized textual transcriptions and strategy annotations for direct comparison.
 
@@
 
-The _Werewolf Arena_ dataset [@bailisWerewolfArenaCase2024] features simulated classic Werewolf games played by LLM agents without human intervention.
-Unlike the one-round human games, these simulations involve multiple rounds alternating between night (secret actions) and day (open discussion).
-Each LLM agent is assigned a role (Villager, Werewolf, Seer, Doctor) and receives context-specific prompts that guide their strategic interactions.
+The *Werewolf Arena* dataset \[@bailisWerewolfArenaCase2024] comprises simulated classic Werewolf games played by autonomous LLM agents.
+Unlike one-round human games, these simulations include multiple rounds alternating between night (secret actions) and day (open discussion).
+Each agent receives a role (Villager, Werewolf, Seer, Doctor) and interacts through tailored prompts generated via an LLM API.
 
-We ran simulations using five LLM models: GPT-4o, GPT-4.1, GPT-4o-mini, DeepSeek-Chat, and DeepSeek-Reasoner. We experimented with two configurations:
+We conducted simulations using five LLM models: GPT-4o, GPT-4.1, GPT-4o-mini, DeepSeek-Chat, and DeepSeek-Reasoner. Two configurations were tested:
 
-- 8 players with 8 rounds of discussion
+* 8 players with 8 discussion rounds
+* 10 players with 6 discussion rounds
 
-- 10 players with 6 rounds of discussion
+We selected these settings to provide ample opportunity for villagers to coordinate and demonstrate persuasive behaviors.
 
-We chose these configurations to give villagers more time to coordinate, extending the dialogue to better observe persuasive behaviors.
-After running the simulations, we manually annotated the LLM-generated dialogue using the same persuasion categories as in the human dataset.
+Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure @fig:wwa-gui.
+The GUI displays the game state, including player roles, actions, and current discussion rounds, enabling monitoring of the gameplay progression.
+
+![GUI of Werewolf Arena simulation](Images/WWA_GUI.PNG.png)
+
+::: {.figure-caption #fig:wwa-gui}
+**Figure 1.** GUI of Werewolf Arena simulation environment.
+:::
+
+A central feature in Werewolf Arena is the dynamic turn-taking system implemented via a bidding mechanism.
+Rather than a fixed speaking order, agents bid for speaking turns based on urgency and strategic necessity, closely simulating real-world group discussions.
+Bidding levels range from passive observation to urgent direct responses:
+
+* 0: Observe quietly
+* 1: Share general thoughts
+* 2: Contribute critical and specific information
+* 3: Urgent need to speak
+* 4: Respond directly after being addressed or accused
+
+The highest bidder speaks next, with ties broken by prioritizing agents directly mentioned in preceding turns.
+This mechanism captures nuanced strategic communication decisions made by agents throughout the game.
+
+Agents utilize specialized prompts reflecting their current role, memory state, and game context.
+The prompts guide strategic interactions, influencing agent decisions in voting, debating, and night actions.
+After generating dialogues through the LLM API, we manually annotated these interactions using the persuasion strategy categories from the human dataset.
 
@@
 
-We standardized annotations across both datasets so they could be directly compared.
-Our analyses focused on frequency distributions of persuasion strategies, comparisons by role (villager versus werewolf), and differences in how humans and LLMs applied these strategies.
+Annotations were standardized across both datasets for direct comparative analysis.
+Our analyses explored frequency distributions of persuasion strategies, role-based comparisons (villager vs.
+werewolf), and strategic differences between human and LLM-generated dialogues.
 

### 2025-05-07 Quarto/paper.qmd
Update Intro, Methods, WWA GUI Figure

@@
 
-Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure @fig:wwa-gui.
+Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure 1.
 The GUI displays the game state, including player roles, actions, and current discussion rounds, enabling monitoring of the gameplay progression.
 
+**Figure 1.** GUI of Werewolf Arena simulation environment.
+
 ![GUI of Werewolf Arena simulation](Images/WWA_GUI.PNG.png)
-
-::: {.figure-caption #fig:wwa-gui}
-**Figure 1.** GUI of Werewolf Arena simulation environment.
-:::
 

### 2025-05-07 Quarto/paper.qmd
Update Intro, Methods, WWA GUI Figure

@@
 
-Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure 1.
+Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure @fig-wwa-gui.
 The GUI displays the game state, including player roles, actions, and current discussion rounds, enabling monitoring of the gameplay progression.
@@
 
-![GUI of Werewolf Arena simulation](Images/WWA_GUI.PNG.png)
+![GUI of Werewolf Arena simulation](Images/WWA_GUI.png){#fig-wwa-gui}
 

### 2025-05-07 _tex/paper.tex
Built site for gh-pages

--- 2025-05-06 _tex/paper.tex
@@
 \author{Bhavana Jonnalagadda \and Riley Jones}
-\date{2025-05-06}
+\date{2025-05-07}
 \begin{document}
@@
 
-\begin{itemize}
-\item
-  Social deduction games like \emph{Werewolf} offer a clear way to
-  evaluate how agents deceive, persuade, and reason in group
-  settings(\citeproc{ref-wikiwerewolf}{Wikipedia contributors 2024}). In
-  these games, players have limited information, hidden identities, and
-  must convince others while trying to figure out who is lying. These
-  challenges closely match real life situations involving trust,
-  negotiation, and manipulation.
-\item
-  We wanted to compare how humans and large language models (LLMs)
-  handle these situations. To do this, we used two recent datasets:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    \emph{Werewolf Among Us} (Lai et al., 2022), a collection of real
-    human gameplay annotated with persuasion strategies,
-  \item
-    \emph{Werewolf Arena} (Bailis et al., 2024), a simulated environment
-    where LLM agents play the game autonomously.
-  \item
-    While both studies show Werewolf generates complex strategic
-    language, neither compares human and LLM behavior directly.
-  \end{itemize}
-\item
-  Our project addresses this gap. We analyzed transcripts from both
-  datasets, matched them by role, round, and persuasion strategy, and
-  compared how humans and LLMs lie, persuade, and detect deception.
-\item
-  By annotating utterances with the same set of persuasive strategies,
-  we clearly show how synthetic agents differ from or resemble humans
-  when navigating deception in adversarial group interactions.
-\end{itemize}
+Social deduction games like Werewolf offer a clear way to evaluate how
+agents deceive, persuade, and reason in group settings
+(\citeproc{ref-wikiwerewolf}{Wikipedia contributors 2024}). In these
+games, players operate with limited information and hidden identities,
+attempting to convince others while trying to uncover deception
+themselves. These dynamics mirror real-world challenges involving trust,
+negotiation, and manipulation. To explore how humans and large language
+models (LLMs) navigate such scenarios, we analyzed two key datasets:
+Werewolf Among Us (\citeproc{ref-laiWerewolfUsMultimodal2022}{Lai et al.
+2022}), which features real human gameplay annotated with persuasion
+strategies, and Werewolf Arena
+(\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and Chen
+2024}), a simulated environment in which LLM agents autonomously play
+the game. While both studies demonstrate that Werewolf elicits rich,
+strategic language, neither directly compares human and LLM behavior.
+Our project fills this gap. We analyzed transcripts from both datasets,
+aligning them by role, round, and persuasive strategy, and compared how
+humans and LLMs lie, persuade, and detect deception. By annotating all
+utterances using a consistent taxonomy of persuasive strategies, we
+expose key differences and similarities in how synthetic agents and
+humans handle adversarial group interactions.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Human dataset description
-  (\citeproc{ref-laiWerewolfUsMultimodal2022}{Lai et al. 2022})
-\item
-  Is specifically for a form of one-night werewolf
+We used the \emph{Werewolf Among Us} dataset {[}Lai et al.
+(\citeproc{ref-laiWerewolfUsMultimodal2022}{2022}){]}, containing
+annotated dialogues from over 150 real games of One Night Werewolf and
+Avalon. These games differ from classic Werewolf by having only one
+round of discussion and voting, not eliminating players during gameplay,
+and featuring specialized roles beyond Villager and Werewolf. The
+dataset includes detailed annotations of persuasion strategies for each
+utterance, such as accusations, defenses, and identity claims. Our
+analysis specifically utilized textual transcriptions and strategy
+annotations for direct comparison.
+
+\subsection{Werewolf Arena (LLM
+Dataset)}\label{werewolf-arena-llm-dataset}
+
+The \emph{Werewolf Arena} dataset {[}Bailis, Friedhoff, and Chen
+(\citeproc{ref-bailisWerewolfArenaCase2024}{2024}){]} comprises
+simulated classic Werewolf games played by autonomous LLM agents. Unlike
+one-round human games, these simulations include multiple rounds
+alternating between night (secret actions) and day (open discussion).
+Each agent receives a role (Villager, Werewolf, Seer, Doctor) and
+interacts through tailored prompts generated via an LLM API.
+
+We conducted simulations using five LLM models: GPT-4o, GPT-4.1,
+GPT-4o-mini, DeepSeek-Chat, and DeepSeek-Reasoner. Two configurations
+were tested:
 
@@
 \item
-    Describe key differences
+  8 players with 8 discussion rounds
+\item
+  10 players with 6 discussion rounds
 \end{itemize}
-\item
-  Used specifically for the text available
+
+We selected these settings to provide ample opportunity for villagers to
+coordinate and demonstrate persuasive behaviors.
+
+Agents participated in gameplay through a graphical user interface
+(GUI), depicted in Figure Figure~\ref{fig-wwa-gui}. The GUI displays the
+game state, including player roles, actions, and current discussion
+rounds, enabling monitoring of the gameplay progression.
+
+\textbf{Figure 1.} GUI of Werewolf Arena simulation environment.
+
+\begin{figure}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{Images/WWA_GUI.png}}
+
+}
+
+\caption{\label{fig-wwa-gui}GUI of Werewolf Arena simulation}
+
+\end{figure}%
+
+A central feature in Werewolf Arena is the dynamic turn-taking system
+implemented via a bidding mechanism. Rather than a fixed speaking order,
+agents bid for speaking turns based on urgency and strategic necessity,
+closely simulating real-world group discussions. Bidding levels range
+from passive observation to urgent direct responses:
 
@@
 \item
-    and annotations of persuasion strategy on the text
-  \end{itemize}
+  0: Observe quietly
+\item
+  1: Share general thoughts
+\item
+  2: Contribute critical and specific information
+\item
+  3: Urgent need to speak
+\item
+  4: Respond directly after being addressed or accused
 \end{itemize}
 
-\subsection{Werewolf Arena}\label{werewolf-arena}
+The highest bidder speaks next, with ties broken by prioritizing agents
+directly mentioned in preceding turns. This mechanism captures nuanced
+strategic communication decisions made by agents throughout the game.
 
-\begin{itemize}
-\tightlist
-\item
-  (\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and
-  Chen 2024})
-\item
-  Discuss the framework, how it works, prompts, etc
-\item
-  Discuss what types of runs we did
-\item
-  Discuss the data included in output
-\item
-  Talk about how we had to annotate the LLM speech with persuasion
-  strategies ourselves
-\end{itemize}
+Agents utilize specialized prompts reflecting their current role, memory
+state, and game context. The prompts guide strategic interactions,
+influencing agent decisions in voting, debating, and night actions.
+After generating dialogues through the LLM API, we manually annotated
+these interactions using the persuasion strategy categories from the
+human dataset.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Formatted data to match, performed various comparisons
-\end{itemize}
+Annotations were standardized across both datasets for direct
+comparative analysis. Our analyses explored frequency distributions of
+persuasion strategies, role-based comparisons (villager vs.~werewolf),
+and strategic differences between human and LLM-generated dialogues.
 

### 2025-05-07 Quarto/paper.qmd
fixing quarto errors
Update Related Works

@@
 
-### Multi-Agent LLMs
+Recent research into multi-agent large language models (LLMs) has explored their performance in various social deduction and collective problem-solving contexts.
+Chi et al.
+\[@chiAMONGAGENTSEvaluatingLarge2024] investigated LLM behavior in the popular game Among Us, revealing capabilities in understanding complex game dynamics and successfully navigating roles involving deception and cooperation.
+Similarly, Du et al.
+\[@duLargeLanguageModels2024] examined collective problem-solving scenarios, finding that LLM agent groups showed increased complexity in their interactions, more frequent disagreements, and generally positive exchanges compared to human groups.
+Piatti et al.
+\[@piattiCooperateCollapseEmergence2024], through the GovSim environment, studied how AI societies managed collective resources, demonstrating that LLM agents effectively balanced ethical considerations, strategic planning, and negotiation, further supporting the idea of their advanced cooperative and strategic capabilities.
 
-- Among us game [@chiAMONGAGENTSEvaluatingLarge2024]
-- Collective problem solving [@duLargeLanguageModels2024]
-  - "analyses indicate that LLM agent groups exhibit more disagreements, complex statements, and a propensity for positive statements compared to human groups"
-- Govsim [@piattiCooperateCollapseEmergence2024]
-  - "In GOVSIM, a society of AI agents must collectively balance exploiting a common resource with sustaining it for future use.
-This environment enables the study of how ethical considerations, strategic planning, and negotiation skills impact cooperative outcomes."
-- All found similar themes
-  - That LLMs are capable and good at understanding the rules
-  - That they can cooperate and be sneaky
-
-### LLMs and Werewolf
-
-- Examination of improving werewolf by LLMs [@xuLanguageAgentsReinforcement2024]
-  - "our agents use an LLM to perform deductive reasoning and generate a diverse set of action candidates.
-Then an RL policy trained to optimize the decision-making ability chooses an action from the candidates to play in the game.
-Extensive experiments show that our agents overcome the intrinsic bias and outperform existing LLM-based agents in the Werewolf game."
-- Werewolf Arena [@bailisWerewolfArenaCase2024]
-  - Used in this paper
-- Explicitly discuss how none of the exisiting LLM+Werewolf papers examine the differences/compare from a human dataset
+Within the specific context of Werewolf, several studies have addressed the use of LLMs to enhance gameplay.
+Xu et al.
+\[@xuLanguageAgentsReinforcement2024] developed LLM agents that leverage deductive reasoning and reinforcement learning to optimize decision-making and gameplay strategy, outperforming existing methods.
+Meanwhile, Bailis et al.
+\[@bailisWerewolfArenaCase2024] introduced the Werewolf Arena, a framework employed in our current study.
+However, despite these advancements, previous research has not explicitly examined or compared LLM-driven Werewolf gameplay to authentic human interactions and strategies.
+Our paper specifically addresses this gap by directly comparing human gameplay, sourced from the Werewolf Among Us dataset, with simulated gameplay generated by LLMs, providing novel insights into differences and similarities in persuasion strategies and social reasoning between humans and AI.
 
@@
 
-Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure @fig-wwa-gui.
+Agents participated in gameplay through a graphical user interface (GUI), depicted in @fig-wwa-gui.
 The GUI displays the game state, including player roles, actions, and current discussion rounds, enabling monitoring of the gameplay progression.
-
-**Figure 1.** GUI of Werewolf Arena simulation environment.
 

### 2025-05-07 _tex/paper.tex
Built site for gh-pages

@@
 
-\subsection{Multi-Agent LLMs}\label{multi-agent-llms}
+Recent research into multi-agent large language models (LLMs) has
+explored their performance in various social deduction and collective
+problem-solving contexts. Chi et al.~{[}Chi, Mao, and Tang
+(\citeproc{ref-chiAMONGAGENTSEvaluatingLarge2024}{2024}){]} investigated
+LLM behavior in the popular game Among Us, revealing capabilities in
+understanding complex game dynamics and successfully navigating roles
+involving deception and cooperation. Similarly, Du et al.~{[}Du,
+Rajivan, and Gonzalez
+(\citeproc{ref-duLargeLanguageModels2024}{2024}){]} examined collective
+problem-solving scenarios, finding that LLM agent groups showed
+increased complexity in their interactions, more frequent disagreements,
+and generally positive exchanges compared to human groups. Piatti et
+al.~{[}Piatti et al.
+(\citeproc{ref-piattiCooperateCollapseEmergence2024}{2024}){]}, through
+the GovSim environment, studied how AI societies managed collective
+resources, demonstrating that LLM agents effectively balanced ethical
+considerations, strategic planning, and negotiation, further supporting
+the idea of their advanced cooperative and strategic capabilities.
 
-\begin{itemize}
-\tightlist
-\item
-  Among us game (\citeproc{ref-chiAMONGAGENTSEvaluatingLarge2024}{Chi,
-  Mao, and Tang 2024})
-\item
-  Collective problem solving
-  (\citeproc{ref-duLargeLanguageModels2024}{Du, Rajivan, and Gonzalez
-  2024})
-
-  \begin{itemize}
-  \tightlist
-  \item
-    ``analyses indicate that LLM agent groups exhibit more
-    disagreements, complex statements, and a propensity for positive
-    statements compared to human groups''
-  \end{itemize}
-\item
-  Govsim (\citeproc{ref-piattiCooperateCollapseEmergence2024}{Piatti et
-  al. 2024})
-
-  \begin{itemize}
-  \tightlist
-  \item
-    ``In GOVSIM, a society of AI agents must collectively balance
-    exploiting a common resource with sustaining it for future use. This
-    environment enables the study of how ethical considerations,
-    strategic planning, and negotiation skills impact cooperative
-    outcomes.''
-  \end{itemize}
-\item
-  All found similar themes
-
-  \begin{itemize}
-  \tightlist
-  \item
-    That LLMs are capable and good at understanding the rules
-  \item
-    That they can cooperate and be sneaky
-  \end{itemize}
-\end{itemize}
-
-\subsection{LLMs and Werewolf}\label{llms-and-werewolf}
-
-\begin{itemize}
-\tightlist
-\item
-  Examination of improving werewolf by LLMs
-  (\citeproc{ref-xuLanguageAgentsReinforcement2024}{Xu et al. 2024})
-
-  \begin{itemize}
-  \tightlist
-  \item
-    ``our agents use an LLM to perform deductive reasoning and generate
-    a diverse set of action candidates. Then an RL policy trained to
-    optimize the decision-making ability chooses an action from the
-    candidates to play in the game. Extensive experiments show that our
-    agents overcome the intrinsic bias and outperform existing LLM-based
-    agents in the Werewolf game.''
-  \end{itemize}
-\item
-  Werewolf Arena (\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis,
-  Friedhoff, and Chen 2024})
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Used in this paper
-  \end{itemize}
-\item
-  Explicitly discuss how none of the exisiting LLM+Werewolf papers
-  examine the differences/compare from a human dataset
-\end{itemize}
+Within the specific context of Werewolf, several studies have addressed
+the use of LLMs to enhance gameplay. Xu et al.~{[}Xu et al.
+(\citeproc{ref-xuLanguageAgentsReinforcement2024}{2024}){]} developed
+LLM agents that leverage deductive reasoning and reinforcement learning
+to optimize decision-making and gameplay strategy, outperforming
+existing methods. Meanwhile, Bailis et al.~{[}Bailis, Friedhoff, and
+Chen (\citeproc{ref-bailisWerewolfArenaCase2024}{2024}){]} introduced
+the Werewolf Arena, a framework employed in our current study. However,
+despite these advancements, previous research has not explicitly
+examined or compared LLM-driven Werewolf gameplay to authentic human
+interactions and strategies. Our paper specifically addresses this gap
+by directly comparing human gameplay, sourced from the Werewolf Among Us
+dataset, with simulated gameplay generated by LLMs, providing novel
+insights into differences and similarities in persuasion strategies and
+social reasoning between humans and AI.
 
@@
 Agents participated in gameplay through a graphical user interface
-(GUI), depicted in Figure Figure~\ref{fig-wwa-gui}. The GUI displays the
-game state, including player roles, actions, and current discussion
-rounds, enabling monitoring of the gameplay progression.
-
-\textbf{Figure 1.} GUI of Werewolf Arena simulation environment.
+(GUI), depicted in Figure~\ref{fig-wwa-gui}. The GUI displays the game
+state, including player roles, actions, and current discussion rounds,
+enabling monitoring of the gameplay progression.
 

### 2025-05-08 Quarto/paper.qmd
Minor edits

@@
 
-Social deduction games like Werewolf offer a clear way to evaluate how agents deceive, persuade, and reason in group settings [@wikiwerewolf].
+Social deduction games like Werewolf [@wikiwerewolf] offer a clear way to evaluate how agents deceive, persuade, and reason in group settings [@stepputtis2023longhorizon].
 In these games, players operate with limited information and hidden identities, attempting to convince others while trying to uncover deception themselves.
@@
 While both studies demonstrate that Werewolf elicits rich, strategic language, neither directly compares human and LLM behavior.
+
 Our project fills this gap.
@@
 Recent research into multi-agent large language models (LLMs) has explored their performance in various social deduction and collective problem-solving contexts.
-Chi et al.
-\[@chiAMONGAGENTSEvaluatingLarge2024] investigated LLM behavior in the popular game Among Us, revealing capabilities in understanding complex game dynamics and successfully navigating roles involving deception and cooperation.
+[@chiAMONGAGENTSEvaluatingLarge2024] investigated LLM behavior in the popular game Among Us, revealing capabilities in understanding complex game dynamics and successfully navigating roles involving deception and cooperation.
 Similarly, Du et al.
-\[@duLargeLanguageModels2024] examined collective problem-solving scenarios, finding that LLM agent groups showed increased complexity in their interactions, more frequent disagreements, and generally positive exchanges compared to human groups.
-Piatti et al.
-\[@piattiCooperateCollapseEmergence2024], through the GovSim environment, studied how AI societies managed collective resources, demonstrating that LLM agents effectively balanced ethical considerations, strategic planning, and negotiation, further supporting the idea of their advanced cooperative and strategic capabilities.
+[@duLargeLanguageModels2024] examined collective problem-solving scenarios, finding that LLM agent groups showed increased complexity in their interactions, more frequent disagreements, and generally positive exchanges compared to human groups.[@piattiCooperateCollapseEmergence2024], through the GovSim environment, studied how AI societies managed collective resources, demonstrating that LLM agents effectively balanced ethical considerations, strategic planning, and negotiation, further supporting the idea of their advanced cooperative and strategic capabilities.
 
 Within the specific context of Werewolf, several studies have addressed the use of LLMs to enhance gameplay.
-Xu et al.
-\[@xuLanguageAgentsReinforcement2024] developed LLM agents that leverage deductive reasoning and reinforcement learning to optimize decision-making and gameplay strategy, outperforming existing methods.
-Meanwhile, Bailis et al.
-\[@bailisWerewolfArenaCase2024] introduced the Werewolf Arena, a framework employed in our current study.
+[@xuLanguageAgentsReinforcement2024] developed LLM agents that leverage deductive reasoning and reinforcement learning to optimize decision-making and gameplay strategy, outperforming existing methods.
+Meanwhile, [@bailisWerewolfArenaCase2024] introduced the Werewolf Arena, a framework employed in our current study.
 However, despite these advancements, previous research has not explicitly examined or compared LLM-driven Werewolf gameplay to authentic human interactions and strategies.
-Our paper specifically addresses this gap by directly comparing human gameplay, sourced from the Werewolf Among Us dataset, with simulated gameplay generated by LLMs, providing novel insights into differences and similarities in persuasion strategies and social reasoning between humans and AI.
 
@@
 
-We used the *Werewolf Among Us* dataset \[@laiWerewolfUsMultimodal2022], containing annotated dialogues from over 150 real games of One Night Werewolf and Avalon.
+We used the *Werewolf Among Us* dataset [@laiWerewolfUsMultimodal2022], containing annotated dialogues from over 150 real games of One Night Werewolf and Avalon.
 These games differ from classic Werewolf by having only one round of discussion and voting, not eliminating players during gameplay, and featuring specialized roles beyond Villager and Werewolf.
 The dataset includes detailed annotations of persuasion strategies for each utterance, such as accusations, defenses, and identity claims.
-Our analysis specifically utilized textual transcriptions and strategy annotations for direct comparison.
+Our analysis specifically used textual transcriptions and strategy annotations for direct comparison.
 
@@
 
-The *Werewolf Arena* dataset \[@bailisWerewolfArenaCase2024] comprises simulated classic Werewolf games played by autonomous LLM agents.
+The *Werewolf Arena* dataset [@bailisWerewolfArenaCase2024] comprises simulated classic Werewolf games played by autonomous LLM agents.
 Unlike one-round human games, these simulations include multiple rounds alternating between night (secret actions) and day (open discussion).
 Each agent receives a role (Villager, Werewolf, Seer, Doctor) and interacts through tailored prompts generated via an LLM API.
-
-We conducted simulations using five LLM models: GPT-4o, GPT-4.1, GPT-4o-mini, DeepSeek-Chat, and DeepSeek-Reasoner. Two configurations were tested:
-
-* 8 players with 8 discussion rounds
-* 10 players with 6 discussion rounds
-
-We selected these settings to provide ample opportunity for villagers to coordinate and demonstrate persuasive behaviors.
-
-Agents participated in gameplay through a graphical user interface (GUI), depicted in @fig-wwa-gui.
-The GUI displays the game state, including player roles, actions, and current discussion rounds, enabling monitoring of the gameplay progression.
-
-![GUI of Werewolf Arena simulation](Images/WWA_GUI.png){#fig-wwa-gui}
 
@@
 
-Agents utilize specialized prompts reflecting their current role, memory state, and game context.
+Agents interact with the game interface via specialized prompts reflecting their current role, memory state, and game context.
 The prompts guide strategic interactions, influencing agent decisions in voting, debating, and night actions.
 After generating dialogues through the LLM API, we manually annotated these interactions using the persuasion strategy categories from the human dataset.
+
+We conducted simulations using five LLM models: GPT-4o, GPT-4.1, GPT-4o-mini, DeepSeek-Chat, and DeepSeek-Reasoner. Two configurations were tested:
+
+* 8 players with 8 discussion rounds
+* 10 players with 6 discussion rounds
+
+We selected these settings to provide ample opportunity for villagers to coordinate and demonstrate persuasive behaviors.
+
+LLM agent gameplay can be viewed and debugged through a graphical user interface (GUI), depicted in @fig-wwa-gui.
+The GUI displays the game state, including player roles, actions, utterances, inner-monologue and current discussion rounds, enabling monitoring of the gameplay progression.
+
+![GUI of Werewolf Arena simulation](Images/WWA_GUI.png){#fig-wwa-gui}
 

### 2025-05-08 _tex/paper.tex
Built site for gh-pages

@@
 \author{Bhavana Jonnalagadda \and Riley Jones}
-\date{2025-05-07}
+\date{2025-05-08}
 \begin{document}
@@
 
-Social deduction games like Werewolf offer a clear way to evaluate how
-agents deceive, persuade, and reason in group settings
-(\citeproc{ref-wikiwerewolf}{Wikipedia contributors 2024}). In these
-games, players operate with limited information and hidden identities,
-attempting to convince others while trying to uncover deception
-themselves. These dynamics mirror real-world challenges involving trust,
-negotiation, and manipulation. To explore how humans and large language
-models (LLMs) navigate such scenarios, we analyzed two key datasets:
-Werewolf Among Us (\citeproc{ref-laiWerewolfUsMultimodal2022}{Lai et al.
-2022}), which features real human gameplay annotated with persuasion
-strategies, and Werewolf Arena
-(\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and Chen
-2024}), a simulated environment in which LLM agents autonomously play
-the game. While both studies demonstrate that Werewolf elicits rich,
-strategic language, neither directly compares human and LLM behavior.
+Social deduction games like Werewolf
+(\citeproc{ref-wikiwerewolf}{Wikipedia contributors 2024}) offer a clear
+way to evaluate how agents deceive, persuade, and reason in group
+settings (\citeproc{ref-stepputtis2023longhorizon}{Stepputtis et al.
+2023}). In these games, players operate with limited information and
+hidden identities, attempting to convince others while trying to uncover
+deception themselves. These dynamics mirror real-world challenges
+involving trust, negotiation, and manipulation. To explore how humans
+and large language models (LLMs) navigate such scenarios, we analyzed
+two key datasets: Werewolf Among Us
+(\citeproc{ref-laiWerewolfUsMultimodal2022}{Lai et al. 2022}), which
+features real human gameplay annotated with persuasion strategies, and
+Werewolf Arena (\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis,
+Friedhoff, and Chen 2024}), a simulated environment in which LLM agents
+autonomously play the game. While both studies demonstrate that Werewolf
+elicits rich, strategic language, neither directly compares human and
+LLM behavior.
+
 Our project fills this gap. We analyzed transcripts from both datasets,
@@
 explored their performance in various social deduction and collective
-problem-solving contexts. Chi et al.~{[}Chi, Mao, and Tang
-(\citeproc{ref-chiAMONGAGENTSEvaluatingLarge2024}{2024}){]} investigated
-LLM behavior in the popular game Among Us, revealing capabilities in
-understanding complex game dynamics and successfully navigating roles
-involving deception and cooperation. Similarly, Du et al.~{[}Du,
-Rajivan, and Gonzalez
-(\citeproc{ref-duLargeLanguageModels2024}{2024}){]} examined collective
-problem-solving scenarios, finding that LLM agent groups showed
-increased complexity in their interactions, more frequent disagreements,
-and generally positive exchanges compared to human groups. Piatti et
-al.~{[}Piatti et al.
-(\citeproc{ref-piattiCooperateCollapseEmergence2024}{2024}){]}, through
-the GovSim environment, studied how AI societies managed collective
-resources, demonstrating that LLM agents effectively balanced ethical
-considerations, strategic planning, and negotiation, further supporting
-the idea of their advanced cooperative and strategic capabilities.
+problem-solving contexts.
+(\citeproc{ref-chiAMONGAGENTSEvaluatingLarge2024}{Chi, Mao, and Tang
+2024}) investigated LLM behavior in the popular game Among Us, revealing
+capabilities in understanding complex game dynamics and successfully
+navigating roles involving deception and cooperation. Similarly, Du et
+al. (\citeproc{ref-duLargeLanguageModels2024}{Du, Rajivan, and Gonzalez
+2024}) examined collective problem-solving scenarios, finding that LLM
+agent groups showed increased complexity in their interactions, more
+frequent disagreements, and generally positive exchanges compared to
+human groups.(\citeproc{ref-piattiCooperateCollapseEmergence2024}{Piatti
+et al. 2024}), through the GovSim environment, studied how AI societies
+managed collective resources, demonstrating that LLM agents effectively
+balanced ethical considerations, strategic planning, and negotiation,
+further supporting the idea of their advanced cooperative and strategic
+capabilities.
 
 Within the specific context of Werewolf, several studies have addressed
-the use of LLMs to enhance gameplay. Xu et al.~{[}Xu et al.
-(\citeproc{ref-xuLanguageAgentsReinforcement2024}{2024}){]} developed
-LLM agents that leverage deductive reasoning and reinforcement learning
-to optimize decision-making and gameplay strategy, outperforming
-existing methods. Meanwhile, Bailis et al.~{[}Bailis, Friedhoff, and
-Chen (\citeproc{ref-bailisWerewolfArenaCase2024}{2024}){]} introduced
-the Werewolf Arena, a framework employed in our current study. However,
-despite these advancements, previous research has not explicitly
-examined or compared LLM-driven Werewolf gameplay to authentic human
-interactions and strategies. Our paper specifically addresses this gap
-by directly comparing human gameplay, sourced from the Werewolf Among Us
-dataset, with simulated gameplay generated by LLMs, providing novel
-insights into differences and similarities in persuasion strategies and
-social reasoning between humans and AI.
+the use of LLMs to enhance gameplay.
+(\citeproc{ref-xuLanguageAgentsReinforcement2024}{Xu et al. 2024})
+developed LLM agents that leverage deductive reasoning and reinforcement
+learning to optimize decision-making and gameplay strategy,
+outperforming existing methods. Meanwhile,
+(\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and Chen
+2024}) introduced the Werewolf Arena, a framework employed in our
+current study. However, despite these advancements, previous research
+has not explicitly examined or compared LLM-driven Werewolf gameplay to
+authentic human interactions and strategies.
 
@@
 
-We used the \emph{Werewolf Among Us} dataset {[}Lai et al.
-(\citeproc{ref-laiWerewolfUsMultimodal2022}{2022}){]}, containing
-annotated dialogues from over 150 real games of One Night Werewolf and
-Avalon. These games differ from classic Werewolf by having only one
-round of discussion and voting, not eliminating players during gameplay,
-and featuring specialized roles beyond Villager and Werewolf. The
-dataset includes detailed annotations of persuasion strategies for each
-utterance, such as accusations, defenses, and identity claims. Our
-analysis specifically utilized textual transcriptions and strategy
+We used the \emph{Werewolf Among Us} dataset
+(\citeproc{ref-laiWerewolfUsMultimodal2022}{Lai et al. 2022}),
+containing annotated dialogues from over 150 real games of One Night
+Werewolf and Avalon. These games differ from classic Werewolf by having
+only one round of discussion and voting, not eliminating players during
+gameplay, and featuring specialized roles beyond Villager and Werewolf.
+The dataset includes detailed annotations of persuasion strategies for
+each utterance, such as accusations, defenses, and identity claims. Our
+analysis specifically used textual transcriptions and strategy
 annotations for direct comparison.
@@
 
-The \emph{Werewolf Arena} dataset {[}Bailis, Friedhoff, and Chen
-(\citeproc{ref-bailisWerewolfArenaCase2024}{2024}){]} comprises
-simulated classic Werewolf games played by autonomous LLM agents. Unlike
-one-round human games, these simulations include multiple rounds
-alternating between night (secret actions) and day (open discussion).
-Each agent receives a role (Villager, Werewolf, Seer, Doctor) and
-interacts through tailored prompts generated via an LLM API.
-
-We conducted simulations using five LLM models: GPT-4o, GPT-4.1,
-GPT-4o-mini, DeepSeek-Chat, and DeepSeek-Reasoner. Two configurations
-were tested:
-
-\begin{itemize}
-\tightlist
-\item
-  8 players with 8 discussion rounds
-\item
-  10 players with 6 discussion rounds
-\end{itemize}
-
-We selected these settings to provide ample opportunity for villagers to
-coordinate and demonstrate persuasive behaviors.
-
-Agents participated in gameplay through a graphical user interface
-(GUI), depicted in Figure~\ref{fig-wwa-gui}. The GUI displays the game
-state, including player roles, actions, and current discussion rounds,
-enabling monitoring of the gameplay progression.
-
-\begin{figure}[H]
-
-\centering{
-
-\pandocbounded{\includegraphics[keepaspectratio]{Images/WWA_GUI.png}}
-
-}
-
-\caption{\label{fig-wwa-gui}GUI of Werewolf Arena simulation}
-
-\end{figure}%
+The \emph{Werewolf Arena} dataset
+(\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and Chen
+2024}) comprises simulated classic Werewolf games played by autonomous
+LLM agents. Unlike one-round human games, these simulations include
+multiple rounds alternating between night (secret actions) and day (open
+discussion). Each agent receives a role (Villager, Werewolf, Seer,
+Doctor) and interacts through tailored prompts generated via an LLM API.
 
@@
 
-Agents utilize specialized prompts reflecting their current role, memory
-state, and game context. The prompts guide strategic interactions,
-influencing agent decisions in voting, debating, and night actions.
-After generating dialogues through the LLM API, we manually annotated
-these interactions using the persuasion strategy categories from the
-human dataset.
+Agents interact with the game interface via specialized prompts
+reflecting their current role, memory state, and game context. The
+prompts guide strategic interactions, influencing agent decisions in
+voting, debating, and night actions. After generating dialogues through
+the LLM API, we manually annotated these interactions using the
+persuasion strategy categories from the human dataset.
+
+We conducted simulations using five LLM models: GPT-4o, GPT-4.1,
+GPT-4o-mini, DeepSeek-Chat, and DeepSeek-Reasoner. Two configurations
+were tested:
+
+\begin{itemize}
+\tightlist
+\item
+  8 players with 8 discussion rounds
+\item
+  10 players with 6 discussion rounds
+\end{itemize}
+
+We selected these settings to provide ample opportunity for villagers to
+coordinate and demonstrate persuasive behaviors.
+
+LLM agent gameplay can be viewed and debugged through a graphical user
+interface (GUI), depicted in Figure~\ref{fig-wwa-gui}. The GUI displays
+the game state, including player roles, actions, utterances,
+inner-monologue and current discussion rounds, enabling monitoring of
+the gameplay progression.
+
+\begin{figure}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{Images/WWA_GUI.png}}
+
+}
+
+\caption{\label{fig-wwa-gui}GUI of Werewolf Arena simulation}
+
+\end{figure}%
 
@@
 
+\bibitem[\citeproctext]{ref-stepputtis2023longhorizon}
+Stepputtis, Simon, Joseph Campbell, Yaqi Xie, Zhengyang Qi, Wenxin
+Sharon Zhang, Ruiyi Wang, Sanketh Rangreji, Charles Michael Lewis, and
+Katia P. Sycara. 2023. {``Long-Horizon Dialogue Understanding for Role
+Identification in the Game of Avalon with Large Language Models.''} In
+\emph{Proceedings of the 2023 Conference on Empirical Methods in Natural
+Language Processing}. \url{https://openreview.net/forum?id=JKmsjKJ0Q8}.
+
 \bibitem[\citeproctext]{ref-wikiwerewolf}

### 2025-05-08 Quarto/paper.qmd
Finish paper

@@
 abstract: |
-  Abstract TODO
+  We present the first direct comparison of human and large language model (LLM) behavior in the classic social deduction game Werewolf, leveraging two annotated datasets: Werewolf Among Us (163 one‐round human games with expert strategy labels) and Werewolf Arena (19 multi‐round LLM simulations across five models).
+Our analyses revealed that LLM agents secure faster, more decisive wins by focusing their communication on direct calls to action, while human players rely on a richer blend of questioning, accusation, defense, and identity claims.
+Despite fewer simulated games, LLMs consistently build consensus within early rounds and show predictable voting patterns, highlighting their strength in rapid coordination under structured prompts.
+However, this comes at the cost of adaptive nuance and evidence‐based persuasion, areas where humans excel through varied strategic interplay.
+Our findings suggest that enhancing future LLM designs with more balanced strategy repertoires and integrating hybrid human–AI interactions could yield agents capable of both efficient coordination and context‐sensitive reasoning in adversarial group settings.
 date: last-modified
@@
 Recent research into multi-agent large language models (LLMs) has explored their performance in various social deduction and collective problem-solving contexts.
-[@chiAMONGAGENTSEvaluatingLarge2024] investigated LLM behavior in the popular game Among Us, revealing capabilities in understanding complex game dynamics and successfully navigating roles involving deception and cooperation.
+@chiAMONGAGENTSEvaluatingLarge2024 investigated LLM behavior in the popular game Among Us, revealing capabilities in understanding complex game dynamics and successfully navigating roles involving deception and cooperation.
 Similarly, Du et al.
-[@duLargeLanguageModels2024] examined collective problem-solving scenarios, finding that LLM agent groups showed increased complexity in their interactions, more frequent disagreements, and generally positive exchanges compared to human groups.[@piattiCooperateCollapseEmergence2024], through the GovSim environment, studied how AI societies managed collective resources, demonstrating that LLM agents effectively balanced ethical considerations, strategic planning, and negotiation, further supporting the idea of their advanced cooperative and strategic capabilities.
+[@duLargeLanguageModels2024] examined collective problem-solving scenarios, finding that LLM agent groups showed increased complexity in their interactions, more frequent disagreements, and generally positive exchanges compared to human groups.
+@piattiCooperateCollapseEmergence2024, through the GovSim environment, studied how AI societies managed collective resources, demonstrating that LLM agents effectively balanced ethical considerations, strategic planning, and negotiation, further supporting the idea of their advanced cooperative and strategic capabilities.
 
 Within the specific context of Werewolf, several studies have addressed the use of LLMs to enhance gameplay.
-[@xuLanguageAgentsReinforcement2024] developed LLM agents that leverage deductive reasoning and reinforcement learning to optimize decision-making and gameplay strategy, outperforming existing methods.
-Meanwhile, [@bailisWerewolfArenaCase2024] introduced the Werewolf Arena, a framework employed in our current study.
+@xuLanguageAgentsReinforcement2024 developed LLM agents that leverage deductive reasoning and reinforcement learning to optimize decision-making and gameplay strategy, outperforming existing methods.
+Meanwhile, @bailisWerewolfArenaCase2024 introduced the Werewolf Arena, a framework employed in our current study.
 However, despite these advancements, previous research has not explicitly examined or compared LLM-driven Werewolf gameplay to authentic human interactions and strategies.
@@
 
+We show example data for both datasets (herefore the "human" and "LLM" datasets respectively) in @tbl-data-hum and @tbl-data-llm, where the data was split by each utterance/speech line into rows.
+
+{{< embed Data/EDA_Comparison.ipynb#tbl-data-hum >}}
+{{< embed Data/EDA_Comparison.ipynb#tbl-data-llm >}}
+
 # Results
 
+## Win Counts
+
+| Source Dataset | Villagers Win  | Number of Games |
+|---------------|---------|-------|
+|LLMs | 57.895%     | 19    |
+|Human| 37.423%     | 163   |
+
+: Whether the Villagers (vs the Werewolves) won a full game. {#tbl-wins .column-margin}
+
+In @tbl-wins, we report the proportion of games won by the villager side and the total number of games analyzed for each dataset.
+The human dataset comprises 163 games drawn from real player sessions, while the LLM simulations were limited to 19 games due to API usage costs associated with generating each additional simulation.
+
+Because LLM gameplay incurs per-call charges, we constrained our LLM sample size to the minimum required for statistical comparison.
+In contrast, the human dataset from Werewolf Among Us provided a larger volume of games at no incremental cost, resulting in a more extensive dataset.
+
+Despite the smaller sample, LLM-driven villagers secured victory in 57.9% of simulated games, compared to a 37.4% win rate for human villagers.
+This suggests that LLM agents, even with limited opportunities, coordinate more effectively or identify werewolves more efficiently than human players.
+Additionally, the narrower confidence interval around the LLM win rate — driven by fewer games — underscores the need for expanded simulation runs in future work to confirm robustness.
+
+### LLM Win Performance
+
+In @fig-wins-bymodel, we observe a clear positive relationship between model complexity and win rate across all roles.
+The most advanced model, GPT-4.1, achieves the highest overall win percentage, whereas simpler or more specialized models like DeepSeek-Chat perform less consistently.
+Because larger models are more expensive to query, we ran fewer simulations for GPT-4o and GPT-4.1, but even with reduced sample sizes their performance gains are pronounced.
+
+@fig-wins-bymodelrole breaks down win rates by both LLM model and assigned role.
+Notably, DeepSeek-Chat underperforms across most roles — particularly Villager, Seer, and Doctor — while showing relative strength only in Werewolf roles.
+Conversely, GPT-4.1 wins in every role except Werewolf, indicating a bias toward non-adversarial coordination behaviors.
+This role-based analysis highlights that some architectures excel at cooperative persuasion but may struggle when tasked with deceptive adversarial play.
+
+@fig-llm-winrounds illustrates the dependence of winning side on game length.
+LLM-driven villagers overwhelmingly secure victories within the first one to two discussion rounds, suggesting they rapidly converge on identifying hidden werewolves.
+As the number of rounds increases, the balance shifts in favor of the werewolves, who capitalize on extended deception opportunities.
+These findings underscore the temporal dynamics of persuasion: early decisive coordination benefits the villagers, while prolonged ambiguity advantages adversaries.
+
+::: {.column-screen-inset layout-ncol="3"}
+{{< embed Data/EDA_Comparison.ipynb#fig-wins-bymodel >}}
+{{< embed Data/EDA_Comparison.ipynb#fig-wins-bymodelrole >}}
 {{< embed Data/EDA_Comparison.ipynb#fig-llm-winrounds >}}
+:::
 
+## Persuasion Strategies
+
+:::: {.columns .column-page-right}
+::: {.column width="40%"}
+In @fig-strat-overall, we compare the distribution of persuasion strategies employed by humans and LLM agents across all utterances.
+Human players display a diverse mix of techniques, with many utterances containing no overt strategy and the rest spread across interrogation, accusation, defense, and identity claims.
+In stark contrast, LLM agents overwhelmingly default to a Call to Action strategy — direct exhortations or voting prompts — with minimal use of defensive language.
+:::
+::: {.column width="60%"}
+{{< embed Data/EDA_Comparison.ipynb#fig-strat-overall >}}
+:::
+::::
+
+@fig-stratbyrole-hum and @fig-stratbyrole-llms reveal how strategy preferences vary by player role, scaled by each role's strategy use (for more understandable analysis).
+Human Villagers, Werewolves, Seers, and Doctors all rely heavily on Interrogation, followed by Accusation and then Defense; notably, Villagers stand out with a higher incidence of Identity Declaration, likely reflecting their need to build trust through role claims.
+Among LLM agents, Call to Action dominates every role, though Werewolves use Interrogation more frequently than their counterparts and Doctors uniquely favor Defense over Evidence when justifying their night actions.
+
+::: {.column-page layout-ncol=2}
 {{< embed Data/EDA_Comparison.ipynb#fig-stratbyrole-hum >}}
 {{< embed Data/EDA_Comparison.ipynb#fig-stratbyrole-llms >}}
+:::
+
+:::: {.columns .column-page-right}
+::: {.column width="60%"}
+{{< embed Data/EDA_Comparison.ipynb#fig-llm-stratbyround >}}
+:::
+::: {.column width="40%"}
+@fig-llm-stratbyround examines how LLM persuasion evolves over the course of a game.
+Early rounds are marked by intense Call to Action and Interrogation strategies, as agents strive to influence voting and gather information.
+As discussions progress, these approaches wane, giving way to increased Identity Declarations, Accusations, and Defenses, indicating a shift toward justification and reputation management in later rounds.
+:::
+::::
+
+## Voting Patterns
+
+To assess whether speaking volume influences suspicion, we plotted vote frequency against utterance count in @fig-talking-hum and @fig-talking-llm.
+Human players who speak more often are indeed more likely to be targeted in votes, suggesting a bias against the most vocal participants.
+LLM agents, however, show little to no correlation between talkativeness and vote count, indicating more uniform voting behavior irrespective of individual participation levels.
+
+{{< embed Data/EDA_Comparison.ipynb#fig-talking-hum >}}
+{{< embed Data/EDA_Comparison.ipynb#fig-talking-llm >}}
+
+:::: {.columns .column-page-right}
+::: {.column width="40%"}
+@fig-voting-spread presents the distribution of vote concentration per round, measured as the ratio of players voting for the most popular choice.
+Human voting patterns are highly variable: some rounds feature unanimous consensus, while others show completely scattered votes.
+In contrast, LLM agents demonstrate more consistency, with 25%–85% of votes typically aligning on the top candidate each round, reflecting predictable decision rules embedded in their prompts and bidding mechanism.
+:::
+::: {.column width="60%"}
+{{< embed Data/EDA_Comparison.ipynb#fig-voting-spread >}}
+:::
+::::
 
@@
 
-Interpret findings, discuss limitations, and propose future work.
+Our comparative analysis reveals that LLM-driven agents not only outperform human players in terms of villager win rates but also exhibit markedly different strategic and behavioral patterns.
+The higher success rate of LLM villagers—winning nearly 58% of games versus 37% for humans—suggests that LLMs are particularly adept at early-round coordination and deduction.
+This is reinforced by the round-by-round win dynamics: LLM villagers overwhelmingly secure victories within the first two discussion rounds, indicating a strong capacity for rapid consensus building.
+In contrast, human teams often extend the game, perhaps reflecting a mix of uncertainty and exploratory dialogue that delays definitive accusations.
+These findings imply that while humans may engage in richer, more varied conversation, LLMs leverage their prompt-driven “Call to Action” strategy to focus discussions quickly around voting decisions, thereby minimizing the window for deception.
+
+However, the dominance of a single persuasion strategy among LLMs also highlights important limitations.
+Unlike humans—who deploy a balanced repertoire of interrogation, accusation, defense, and identity declarations—LLM agents overwhelmingly resort to direct exhortations or voting prompts, with minimal defensive or evidentiary reasoning.
+This narrow strategic palette may contribute to their early-round success yet also points to a lack of adaptive nuance; for instance, LLM werewolves struggle to sustain deception over multiple rounds and rely less on subtle tactics such as identity claims or evidence-based persuasion.
+Similarly, the voting behavior of LLMs, which shows a consistent 25–85% alignment on the top choice each round, contrasts with the broad variability observed in human votes and suggests that agent prompting enforces uniformity at the expense of authentic deliberation.
+Taken together, these insights underscore both the strengths and the rigidities of current LLM architectures in social deduction contexts: they excel at swift coordination under structured prompts, but they lack the flexible, context-sensitive judgment that characterizes human strategic interplay.
+Future work should explore hybrid approaches that blend the decisiveness of LLM-driven voting with the expressive diversity of human persuasion strategies to achieve both efficiency and depth in adversarial group interactions.
 
@@
 
+Despite the insights gained, our study has several important limitations.
+First, the number of LLM-simulated games was constrained by per-call API costs, resulting in only 19 simulated matches versus 163 human games.
+This small sample increases variance in the LLM win‐rate estimates and may obscure subtler patterns of strategic behavior.
+Second, our manual annotation of LLM utterances for persuasion strategy—while guided by the same taxonomy as the human dataset—was necessarily more cursory than the fully expert-validated labels in the Werewolf Among Us corpus.
+As a result, some nuanced tactics or mixed‐strategy turns may have been misclassified or overlooked.
+
+Additionally, the human dataset itself differs from our LLM simulations in fundamental ways: it consists of one-round “One Night” variants with specialized roles and no eliminations, whereas the LLM Arena follows classic multi-round Werewolf rules with eliminations and night actions.
+These structural differences complicate direct comparisons of strategy prevalence and win dynamics.
+Finally, all LLM agents relied on a fixed prompt design and bidding mechanism that may bias them toward certain behaviors (e.g., frequent calls to action); alternative prompt formulations or interactive interfaces could yield different outcomes.
+
 ## Future Work
+
+To address these limitations, future research should expand the scale and diversity of LLM simulations by negotiating lower API costs or leveraging open-source models.
+A larger, more varied set of games would enable finer-grained analysis of how model size, architecture, and cost constraints interact with strategic performance.
+Concurrently, a more rigorous annotation pipeline—potentially incorporating multi-rater agreement or semi-automated classification—could improve the fidelity of strategy labels for LLM dialogue.
+
+We also recommend designing hybrid human–AI experiments in which human players interact directly with LLM agents under controlled conditions.
+Such studies would reveal how LLM persuasion strategies influence, and are influenced by, real human responses.
+Exploring alternative prompt structures, dynamic bidding rules, or reward signals (e.g., reinforcement learning to optimize for deceptive success) could further uncover the boundaries of LLM social reasoning.
+Finally, extending this comparative framework to other social deduction games or negotiation tasks would test the generality of our findings across domains of trust, cooperation, and adversarial persuasion.
 
@@
 
-Summarize contributions and insights from the project.
+In this work, we presented the first direct comparison of human and LLM behavior in the classic Werewolf social deduction game.
+By aligning two annotated datasets—Werewolf Among Us for humans and the custom-simulated Werewolf Arena for LLMs—we evaluated win rates, persuasion strategies, and voting dynamics across roles and rounds.
+Our results demonstrate that LLM agents achieve higher villager win rates, driven by early, prompt-focused “Call to Action” strategies, yet they lack the adaptive nuance and strategic diversity characteristic of human players.
+
+These findings highlight both the promise and rigidity of current large language models in group-level adversarial settings: they excel at rapid coordination but underutilize defensive and evidence-based tactics.
+By identifying key areas for improvement—such as more balanced strategy repertoires, refined annotation methods, and human–AI hybrid studies—we chart a roadmap for enhancing LLM social intelligence and developing richer, more human-like agents in future research.
 

### 2025-05-08 _tex/paper.tex
Built site for gh-pages

@@
   DIV=11,
-  numbers=noendperiod]{scrreprt}
+  numbers=noendperiod,
+  oneside]{scrreprt}
 \usepackage{xcolor}
-\usepackage[margin=0.5in]{geometry}
+\usepackage[left=0.5in,top=0.5in,bottom=0.5in,textwidth=6.5in]{geometry}
 \usepackage{amsmath,amssymb}
@@
 \makeatother
+\makeatletter
+\@ifpackageloaded{sidenotes}{}{\usepackage{sidenotes}}
+\@ifpackageloaded{marginnote}{}{\usepackage{marginnote}}
+\makeatother
 \usepackage{bookmark}
@@
 \begin{abstract}
-Abstract TODO
+We present the first direct comparison of human and large language model
+(LLM) behavior in the classic social deduction game Werewolf, leveraging
+two annotated datasets: Werewolf Among Us (163 one‐round human games
+with expert strategy labels) and Werewolf Arena (19 multi‐round LLM
+simulations across five models). Our analyses revealed that LLM agents
+secure faster, more decisive wins by focusing their communication on
+direct calls to action, while human players rely on a richer blend of
+questioning, accusation, defense, and identity claims. Despite fewer
+simulated games, LLMs consistently build consensus within early rounds
+and show predictable voting patterns, highlighting their strength in
+rapid coordination under structured prompts. However, this comes at the
+cost of adaptive nuance and evidence‐based persuasion, areas where
+humans excel through varied strategic interplay. Our findings suggest
+that enhancing future LLM designs with more balanced strategy
+repertoires and integrating hybrid human--AI interactions could yield
+agents capable of both efficient coordination and context‐sensitive
+reasoning in adversarial group settings.
 \end{abstract}
@@
 explored their performance in various social deduction and collective
-problem-solving contexts.
-(\citeproc{ref-chiAMONGAGENTSEvaluatingLarge2024}{Chi, Mao, and Tang
-2024}) investigated LLM behavior in the popular game Among Us, revealing
-capabilities in understanding complex game dynamics and successfully
-navigating roles involving deception and cooperation. Similarly, Du et
-al. (\citeproc{ref-duLargeLanguageModels2024}{Du, Rajivan, and Gonzalez
+problem-solving contexts. Chi, Mao, and Tang
+(\citeproc{ref-chiAMONGAGENTSEvaluatingLarge2024}{2024}) investigated
+LLM behavior in the popular game Among Us, revealing capabilities in
+understanding complex game dynamics and successfully navigating roles
+involving deception and cooperation. Similarly, Du et al.
+(\citeproc{ref-duLargeLanguageModels2024}{Du, Rajivan, and Gonzalez
 2024}) examined collective problem-solving scenarios, finding that LLM
@@
 frequent disagreements, and generally positive exchanges compared to
-human groups.(\citeproc{ref-piattiCooperateCollapseEmergence2024}{Piatti
-et al. 2024}), through the GovSim environment, studied how AI societies
-managed collective resources, demonstrating that LLM agents effectively
-balanced ethical considerations, strategic planning, and negotiation,
-further supporting the idea of their advanced cooperative and strategic
-capabilities.
+human groups. Piatti et al.
+(\citeproc{ref-piattiCooperateCollapseEmergence2024}{2024}), through the
+GovSim environment, studied how AI societies managed collective
+resources, demonstrating that LLM agents effectively balanced ethical
+considerations, strategic planning, and negotiation, further supporting
+the idea of their advanced cooperative and strategic capabilities.
 
 Within the specific context of Werewolf, several studies have addressed
-the use of LLMs to enhance gameplay.
-(\citeproc{ref-xuLanguageAgentsReinforcement2024}{Xu et al. 2024})
-developed LLM agents that leverage deductive reasoning and reinforcement
-learning to optimize decision-making and gameplay strategy,
-outperforming existing methods. Meanwhile,
-(\citeproc{ref-bailisWerewolfArenaCase2024}{Bailis, Friedhoff, and Chen
-2024}) introduced the Werewolf Arena, a framework employed in our
-current study. However, despite these advancements, previous research
-has not explicitly examined or compared LLM-driven Werewolf gameplay to
-authentic human interactions and strategies.
+the use of LLMs to enhance gameplay. Xu et al.
+(\citeproc{ref-xuLanguageAgentsReinforcement2024}{2024}) developed LLM
+agents that leverage deductive reasoning and reinforcement learning to
+optimize decision-making and gameplay strategy, outperforming existing
+methods. Meanwhile, Bailis, Friedhoff, and Chen
+(\citeproc{ref-bailisWerewolfArenaCase2024}{2024}) introduced the
+Werewolf Arena, a framework employed in our current study. However,
+despite these advancements, previous research has not explicitly
+examined or compared LLM-driven Werewolf gameplay to authentic human
+interactions and strategies.
 
@@
 
+We show example data for both datasets (herefore the ``human'' and
+``LLM'' datasets respectively) in Table~\ref{tbl-data-hum} and
+Table~\ref{tbl-data-llm}, where the data was split by each
+utterance/speech line into rows.
+
+\begin{table*}
+
+\caption{\label{tbl-data-hum}The Werewolf Among Us human dataset, where
+each data row is per utterance.}
+
+\centering{
+
+\begin{tabular}{lllllllllllll}
+\toprule
+~ & Rec\_Id & speaker & timestamp & text & strategy & source & utterance\_length & game\_id & voted\_for & end\_role & votes\_target & winner\\
+\midrule
+6921 & 87 & brett & 219 & I\textquotesingle m 100\% a Villager which
+makes me think he was the Werewolf and he saw Seer in the
+middle. & {[}\textquotesingle Identity Declaration\textquotesingle,
+\textquotesingle Accusation\textquotesingle{]} & Youtube & 19 & game1 -
+One Night Ultimate Werewolf 1 How-To and
+Playthrough & katie & Villager & brett & Werewolves\\
+4013 & 110 & chris & 305 & Wait, but you know- & {[}\textquotesingle No
+Strategy\textquotesingle{]} & Ego4D & 4 & game1 -
+698f6bbe-4347-4a06-bd5d-3482f5e4fbbe & ashley & Drunk & ashley & Villagers\\
+12742 & 76 & dustin & 278 & We\textquotesingle re trying to go,
+we\textquotesingle re...
+What? & {[}\textquotesingle Interrogation\textquotesingle{]} & Youtube & 6 & game1
+- One Night Ultimate Werewolf 382 Game
+100!! & dylan & Werewolf & dylan & Werewolves\\
+3644 & 67 & margaret & 257 & So that means that you were a liar. Which
+makes you a Werewolve.
+Because & {[}\textquotesingle Accusation\textquotesingle{]} & Ego4D & 14 & game8
+-
+2ba4023c-a8bf-43ad-ad5a-80ba222ce990 & erin & Hunter & clint & Villagers\\
+15832 & 76 & mitchell & 291 & That\textquotesingle s all
+I\textquotesingle m
+saying. & {[}\textquotesingle Defense\textquotesingle{]} & Youtube & 4 & game6
+- ONE NIGHT ULTIMATE WEREWOLF Retro
+1 & justin & Robber & justin & Villagers\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{table*}%
+
+\begin{table*}
+
+\caption{\label{tbl-data-llm}The generated Werewolf Arena LLM dataset,
+where each data row is per utterance.}
+
+\centering{
+
+\begin{tabular}{llllllllllllllll}
+\toprule
+~ & players & eliminated & unmasked & protected & exiled & success & game\_id & winner & round & roles & models & speaker & text & timestamp & strategy\\
+\midrule
+270 & {[}\textquotesingle Derek\textquotesingle,
+\textquotesingle Dan\textquotesingle,
+\textquotesingle Jackson\textquotesingle,
+\textquotesingle Jacob\textquotesingle,
+\textquotesingle Leah\textquotesingle{]} & Paul & Sam & nan & Sam & True & 370 & Werewolves & 1 & {[}\textquotesingle Villager\textquotesingle,
+\textquotesingle Villager\textquotesingle,
+\textquotesingle Villager\textquotesingle,
+\textquotesingle Villager\textquotesingle,
+\textquotesingle Werewolf\textquotesingle{]} & {[}\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle,
+\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle,
+\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle,
+\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle,
+\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle{]} & Sam & I
+think it\textquotesingle s crucial to directly address what has been
+said here. Dan and Jacob, while your intentions may seem noble, your
+accusations against both me and Jackson feel premature. Jackson's
+defensiveness about his silence is interesting; it suggests a possible
+awareness of how closely watched he is, perhaps even an effort to divert
+our attention away from him. Why not explore that angle further? It's
+also concerning to me that both of you are so eager to cast the
+spotlight on me rather than taking a broader look at behaviors. In fact,
+I\textquotesingle ve been thinking that we need to channel our
+discussions productively. It seems like Jackson is trying to deflect by
+putting focus on our scrutiny rather than addressing the core issues at
+hand---shouldn\textquotesingle t we be questioning why he feels so
+defensive? If we\textquotesingle re truly going to work together as a
+team, we must evaluate everyone\textquotesingle s actions equally. We
+could simply be underestimating the potential threat that is right in
+front of us. & 11 & {[}\textquotesingle Interrogation\textquotesingle,
+\textquotesingle Accusation\textquotesingle, \textquotesingle Call for
+Action\textquotesingle, \textquotesingle Identity
+Declaration\textquotesingle{]}\\
+5 & {[}\textquotesingle Harold\textquotesingle,
+\textquotesingle Will\textquotesingle,
+\textquotesingle Sam\textquotesingle,
+\textquotesingle Jackson\textquotesingle,
+\textquotesingle Hayley\textquotesingle,
+\textquotesingle Jacob\textquotesingle,
+\textquotesingle Mason\textquotesingle{]} & Dan & Will & Hayley & nan & True & 861 & Werewolves & 0 & {[}\textquotesingle Villager\textquotesingle,
+\textquotesingle Villager\textquotesingle,
+\textquotesingle Villager\textquotesingle,
+\textquotesingle Villager\textquotesingle,
+\textquotesingle Werewolf\textquotesingle,
+\textquotesingle Werewolf\textquotesingle,
+\textquotesingle Doctor\textquotesingle{]} & {[}\textquotesingle gpt-4o-2024-05-13\textquotesingle,
+\textquotesingle gpt-4o-2024-05-13\textquotesingle,
+\textquotesingle gpt-4o-2024-05-13\textquotesingle,
+\textquotesingle gpt-4o-2024-05-13\textquotesingle,
+\textquotesingle gpt-4o-2024-05-13\textquotesingle,
+\textquotesingle gpt-4o-2024-05-13\textquotesingle,
+\textquotesingle gpt-4o-2024-05-13\textquotesingle{]} & Harold & I think
+everyone is bringing up some excellent points. I agree that we need to
+pay close attention to both extremes of behavior---those who are overly
+vocal and those who might be unusually silent. However, let's also be
+cautious not to jump to conclusions too hastily. We need to gather as
+much information as possible. I suggest we keep a mental note of
+everyone\textquotesingle s behavior and remarks. If someone claims to be
+the Seer or Doctor down the line, we should be ready to analyze and
+corroborate their information carefully. For now, let's continue our
+observations and avoid rushing our decisions. Does anyone recall
+anything specific from the night phase or have any gut feelings about
+someone\textquotesingle s behavior so
+far? & 5 & {[}\textquotesingle Interrogation\textquotesingle,
+\textquotesingle Accusation\textquotesingle, \textquotesingle Call for
+Action\textquotesingle{]}\\
+130 & {[}\textquotesingle David\textquotesingle,
+\textquotesingle Bert\textquotesingle,
+\textquotesingle Jacob\textquotesingle,
+\textquotesingle Harold\textquotesingle,
+\textquotesingle Mason\textquotesingle,
+\textquotesingle Will\textquotesingle{]} & Will & Hayley & Will & Hayley & True & 289 & Villagers & 1 & {[}\textquotesingle Villager\textquotesingle,
+\textquotesingle Villager\textquotesingle,
+\textquotesingle Villager\textquotesingle,
+\textquotesingle Werewolf\textquotesingle,
+\textquotesingle Doctor\textquotesingle,
+\textquotesingle Seer\textquotesingle{]} & {[}\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle,
+\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle,
+\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle,
+\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle,
+\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle,
+\textquotesingle gpt-4o-mini-2024-07-18\textquotesingle{]} & Jacob & I
+appreciate the concerns raised about my quietness earlier. Let me
+clarify my position: I'm Jacob, a Villager, and I\textquotesingle m
+committed to working with all of you to identify the Werewolves among
+us. Will has claimed to be the Seer, and I think we should trust him,
+especially since he backed me up without hesitation. Mason's reveal
+about protecting David is another point that adds insight into our
+discussions. We have to pay close attention to Hayley's pushback on
+Will's confidence and my behavior; it seems like a tactic to create
+doubt where we should be building trust. We need to focus on
+collaboration, so how about we scrutinize those who have been less
+vocal? Bert and Harold have echoed concerns about trust, which is
+valuable, but we need to ensure we channel that energy into identifying
+players who are not contributing. Let's come together and form a
+strategy to vote out the Werewolves
+together! & 8 & {[}\textquotesingle No Strategy\textquotesingle{]}\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{table*}%
+
 \chapter{Results}\label{results}
+
+\section{Win Counts}\label{win-counts}
+
+\begin{longtable}[]{@{}lll@{}}
+\caption{Whether the Villagers (vs the Werewolves) won a full
+game.}\label{tbl-wins}\tabularnewline
+\toprule\noalign{}
+Source Dataset & Villagers Win & Number of Games \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Source Dataset & Villagers Win & Number of Games \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+LLMs & 57.895\% & 19 \\
+Human & 37.423\% & 163 \\
+\end{longtable}
+
+In Table~\ref{tbl-wins}, we report the proportion of games won by the
+villager side and the total number of games analyzed for each dataset.
+The human dataset comprises 163 games drawn from real player sessions,
+while the LLM simulations were limited to 19 games due to API usage
+costs associated with generating each additional simulation.
+
+Because LLM gameplay incurs per-call charges, we constrained our LLM
+sample size to the minimum required for statistical comparison. In
+contrast, the human dataset from Werewolf Among Us provided a larger
+volume of games at no incremental cost, resulting in a more extensive
+dataset.
+
+Despite the smaller sample, LLM-driven villagers secured victory in
+57.9\% of simulated games, compared to a 37.4\% win rate for human
+villagers. This suggests that LLM agents, even with limited
+opportunities, coordinate more effectively or identify werewolves more
+efficiently than human players. Additionally, the narrower confidence
+interval around the LLM win rate --- driven by fewer games ---
+underscores the need for expanded simulation runs in future work to
+confirm robustness.
+
+\subsection{LLM Win Performance}\label{llm-win-performance}
+
+In Figure~\ref{fig-wins-bymodel}, we observe a clear positive
+relationship between model complexity and win rate across all roles. The
+most advanced model, GPT-4.1, achieves the highest overall win
+percentage, whereas simpler or more specialized models like
+DeepSeek-Chat perform less consistently. Because larger models are more
+expensive to query, we ran fewer simulations for GPT-4o and GPT-4.1, but
+even with reduced sample sizes their performance gains are pronounced.
+
+Figure~\ref{fig-wins-bymodelrole} breaks down win rates by both LLM
+model and assigned role. Notably, DeepSeek-Chat underperforms across
+most roles --- particularly Villager, Seer, and Doctor --- while showing
+relative strength only in Werewolf roles. Conversely, GPT-4.1 wins in
+every role except Werewolf, indicating a bias toward non-adversarial
+coordination behaviors. This role-based analysis highlights that some
+architectures excel at cooperative persuasion but may struggle when
+tasked with deceptive adversarial play.
+
+Figure~\ref{fig-llm-winrounds} illustrates the dependence of winning
+side on game length. LLM-driven villagers overwhelmingly secure
+victories within the first one to two discussion rounds, suggesting they
+rapidly converge on identifying hidden werewolves. As the number of
+rounds increases, the balance shifts in favor of the werewolves, who
+capitalize on extended deception opportunities. These findings
+underscore the temporal dynamics of persuasion: early decisive
+coordination benefits the villagers, while prolonged ambiguity
+advantages adversaries.
+
+\begin{figure*}
+
+\begin{minipage}{0.33\linewidth}
 
@@
 
-\subcaption{\label{fig-llm-winrounds-1}The LLM wins, by how many rounds
-that partiticular game had.}
+\subcaption{\label{fig-wins-bymodel-1}}
 
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-llm-winrounds-output-2.png}}
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-wins-bymodel-output-2.png}}
 
@@
 
-\subcaption{\label{fig-llm-winrounds-2}}
+\subcaption{\label{fig-wins-bymodel-2}}
 
@@
 
-\caption{\label{fig-llm-winrounds}}
+\caption{\label{fig-wins-bymodel}}
 
@@
 
-\textsubscript{Source:
-\href{https://CUBoulder-DS.github.io/CSCI-5423-Final/Data/EDA_Comparison-preview.html\#cell-fig-llm-winrounds}{Werewolf
-Among Us: Human vs LLM Analysis}}
+\end{minipage}%
+%
+\begin{minipage}{0.33\linewidth}
+
+\begin{figure}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-wins-bymodelrole-output-1.png}}
+
+}
+
+\caption{\label{fig-wins-bymodelrole}}
+
+\end{figure}%
+
+\end{minipage}%
+%
+\begin{minipage}{0.33\linewidth}
+
+\begin{figure}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-llm-winrounds-output-1.png}}
+
+}
+
+\caption{\label{fig-llm-winrounds}The LLM wins, by how many rounds that
+partiticular game had.}
+
+\end{figure}%
+
+\end{minipage}%
+
+\end{figure*}%
+
+\section{Persuasion Strategies}\label{persuasion-strategies}
+
+\begin{figure*}
+
+In Figure~\ref{fig-strat-overall}, we compare the distribution of
+persuasion strategies employed by humans and LLM agents across all
+utterances. Human players display a diverse mix of techniques, with many
+utterances containing no overt strategy and the rest spread across
+interrogation, accusation, defense, and identity claims. In stark
+contrast, LLM agents overwhelmingly default to a Call to Action strategy
+--- direct exhortations or voting prompts --- with minimal use of
+defensive language.
+
+\begin{figure}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-strat-overall-output-1.png}}
+
+}
+
+\caption{\label{fig-strat-overall}The persuasion strategies used by
+humans vs LLMs; scales are seperate per dataset for more even
+comparison.}
+
+\end{figure}%
+
+\end{figure*}%
+
+Figure~\ref{fig-stratbyrole-hum} and Figure~\ref{fig-stratbyrole-llms}
+reveal how strategy preferences vary by player role, scaled by each
+role's strategy use (for more understandable analysis). Human Villagers,
+Werewolves, Seers, and Doctors all rely heavily on Interrogation,
+followed by Accusation and then Defense; notably, Villagers stand out
+with a higher incidence of Identity Declaration, likely reflecting their
+need to build trust through role claims. Among LLM agents, Call to
+Action dominates every role, though Werewolves use Interrogation more
+frequently than their counterparts and Doctors uniquely favor Defense
+over Evidence when justifying their night actions.
+
+\begin{figure*}
+
+\begin{minipage}{0.50\linewidth}
 
@@
 
-\textsubscript{Source:
-\href{https://CUBoulder-DS.github.io/CSCI-5423-Final/Data/EDA_Comparison-preview.html\#cell-fig-stratbyrole-hum}{Werewolf
-Among Us: Human vs LLM Analysis}}
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
 
@@
 
-\textsubscript{Source:
-\href{https://CUBoulder-DS.github.io/CSCI-5423-Final/Data/EDA_Comparison-preview.html\#cell-fig-stratbyrole-llms}{Werewolf
-Among Us: Human vs LLM Analysis}}
+\end{minipage}%
+
+\end{figure*}%
+
+\begin{figure*}
+
+\begin{figure}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-llm-stratbyround-output-1.png}}
+
+}
+
+\caption{\label{fig-llm-stratbyround}}
+
+\end{figure}%
+
+Figure~\ref{fig-llm-stratbyround} examines how LLM persuasion evolves
+over the course of a game. Early rounds are marked by intense Call to
+Action and Interrogation strategies, as agents strive to influence
+voting and gather information. As discussions progress, these approaches
+wane, giving way to increased Identity Declarations, Accusations, and
+Defenses, indicating a shift toward justification and reputation
+management in later rounds.
+
+\end{figure*}%
+
+\section{Voting Patterns}\label{voting-patterns}
+
+To assess whether speaking volume influences suspicion, we plotted vote
+frequency against utterance count in Figure~\ref{fig-talking-hum} and
+Figure~\ref{fig-talking-llm}. Human players who speak more often are
+indeed more likely to be targeted in votes, suggesting a bias against
+the most vocal participants. LLM agents, however, show little to no
+correlation between talkativeness and vote count, indicating more
+uniform voting behavior irrespective of individual participation levels.
+
+\begin{figure*}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-talking-hum-output-1.png}}
+
+}
+
+\caption{\label{fig-talking-hum}}
+
+\end{figure*}%
+
+\begin{figure*}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-talking-llm-output-1.png}}
+
+}
+
+\caption{\label{fig-talking-llm}}
+
+\end{figure*}%
+
+\begin{figure*}
+
+Figure~\ref{fig-voting-spread} presents the distribution of vote
+concentration per round, measured as the ratio of players voting for the
+most popular choice. Human voting patterns are highly variable: some
+rounds feature unanimous consensus, while others show completely
+scattered votes. In contrast, LLM agents demonstrate more consistency,
+with 25\%--85\% of votes typically aligning on the top candidate each
+round, reflecting predictable decision rules embedded in their prompts
+and bidding mechanism.
+
+\begin{figure}[H]
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-latex/Data-EDA_Comparison-fig-voting-spread-output-1.png}}
+
+}
+
+\caption{\label{fig-voting-spread}}
+
+\end{figure}%
+
+\end{figure*}%
 
@@
 
-Interpret findings, discuss limitations, and propose future work.
+Our comparative analysis reveals that LLM-driven agents not only
+outperform human players in terms of villager win rates but also exhibit
+markedly different strategic and behavioral patterns. The higher success
+rate of LLM villagers---winning nearly 58\% of games versus 37\% for
+humans---suggests that LLMs are particularly adept at early-round
+coordination and deduction. This is reinforced by the round-by-round win
+dynamics: LLM villagers overwhelmingly secure victories within the first
+two discussion rounds, indicating a strong capacity for rapid consensus
+building. In contrast, human teams often extend the game, perhaps
+reflecting a mix of uncertainty and exploratory dialogue that delays
+definitive accusations. These findings imply that while humans may
+engage in richer, more varied conversation, LLMs leverage their
+prompt-driven ``Call to Action'' strategy to focus discussions quickly
+around voting decisions, thereby minimizing the window for deception.
+
+However, the dominance of a single persuasion strategy among LLMs also
+highlights important limitations. Unlike humans---who deploy a balanced
+repertoire of interrogation, accusation, defense, and identity
+declarations---LLM agents overwhelmingly resort to direct exhortations
+or voting prompts, with minimal defensive or evidentiary reasoning. This
+narrow strategic palette may contribute to their early-round success yet
+also points to a lack of adaptive nuance; for instance, LLM werewolves
+struggle to sustain deception over multiple rounds and rely less on
+subtle tactics such as identity claims or evidence-based persuasion.
+Similarly, the voting behavior of LLMs, which shows a consistent
+25--85\% alignment on the top choice each round, contrasts with the
+broad variability observed in human votes and suggests that agent
+prompting enforces uniformity at the expense of authentic deliberation.
+Taken together, these insights underscore both the strengths and the
+rigidities of current LLM architectures in social deduction contexts:
+they excel at swift coordination under structured prompts, but they lack
+the flexible, context-sensitive judgment that characterizes human
+strategic interplay. Future work should explore hybrid approaches that
+blend the decisiveness of LLM-driven voting with the expressive
+diversity of human persuasion strategies to achieve both efficiency and
+depth in adversarial group interactions.
 
@@
 
+Despite the insights gained, our study has several important
+limitations. First, the number of LLM-simulated games was constrained by
+per-call API costs, resulting in only 19 simulated matches versus 163
+human games. This small sample increases variance in the LLM win‐rate
+estimates and may obscure subtler patterns of strategic behavior.
+Second, our manual annotation of LLM utterances for persuasion
+strategy---while guided by the same taxonomy as the human dataset---was
+necessarily more cursory than the fully expert-validated labels in the
+Werewolf Among Us corpus. As a result, some nuanced tactics or
+mixed‐strategy turns may have been misclassified or overlooked.
+
+Additionally, the human dataset itself differs from our LLM simulations
+in fundamental ways: it consists of one-round ``One Night'' variants
+with specialized roles and no eliminations, whereas the LLM Arena
+follows classic multi-round Werewolf rules with eliminations and night
+actions. These structural differences complicate direct comparisons of
+strategy prevalence and win dynamics. Finally, all LLM agents relied on
+a fixed prompt design and bidding mechanism that may bias them toward
+certain behaviors (e.g., frequent calls to action); alternative prompt
+formulations or interactive interfaces could yield different outcomes.
+
 \section{Future Work}\label{future-work}
+
+To address these limitations, future research should expand the scale
+and diversity of LLM simulations by negotiating lower API costs or
+leveraging open-source models. A larger, more varied set of games would
+enable finer-grained analysis of how model size, architecture, and cost
+constraints interact with strategic performance. Concurrently, a more
+rigorous annotation pipeline---potentially incorporating multi-rater
+agreement or semi-automated classification---could improve the fidelity
+of strategy labels for LLM dialogue.
+
+We also recommend designing hybrid human--AI experiments in which human
+players interact directly with LLM agents under controlled conditions.
+Such studies would reveal how LLM persuasion strategies influence, and
+are influenced by, real human responses. Exploring alternative prompt
+structures, dynamic bidding rules, or reward signals (e.g.,
+reinforcement learning to optimize for deceptive success) could further
+uncover the boundaries of LLM social reasoning. Finally, extending this
+comparative framework to other social deduction games or negotiation
+tasks would test the generality of our findings across domains of trust,
+cooperation, and adversarial persuasion.
 
@@
 
-Summarize contributions and insights from the project.
+In this work, we presented the first direct comparison of human and LLM
+behavior in the classic Werewolf social deduction game. By aligning two
+annotated datasets---Werewolf Among Us for humans and the
+custom-simulated Werewolf Arena for LLMs---we evaluated win rates,
+persuasion strategies, and voting dynamics across roles and rounds. Our
+results demonstrate that LLM agents achieve higher villager win rates,
+driven by early, prompt-focused ``Call to Action'' strategies, yet they
+lack the adaptive nuance and strategic diversity characteristic of human
+players.
+
+These findings highlight both the promise and rigidity of current large
+language models in group-level adversarial settings: they excel at rapid
+coordination but underutilize defensive and evidence-based tactics. By
+identifying key areas for improvement---such as more balanced strategy
+repertoires, refined annotation methods, and human--AI hybrid
+studies---we chart a roadmap for enhancing LLM social intelligence and
+developing richer, more human-like agents in future research.
 
